---
title: "Code for thesis: Assessing spatial and temporal variability in crop response to bio-based and mineral fertilisers, using remote sensing"
author: "Peter Vingum"
format: html
editor: visual
---

# Code for thesis: Assessing spatial and temporal variability in crop response to bio-based and mineral fertilisers, using remote sensing

Code created by Peter Vingum.

## Introduction

In the following document i have tried to collect all code used for assessing the questions related to the thesis. I will try to annotate, but excuse if it is not straightforward to follow.

## Setup

### Loading libraries

```{r}
#Loading libraries
library(here)
library(fs)
library(ggplot2)
library(knitr)
library(kableExtra)
library(tidyverse)
library(lme4)
library(car)
library(emmeans)
library(broom)
library(patchwork)
library(nlme)
library(stringr)
library(mgcv)
library(multcompView)
library(lubridate)
library(ggpubr)
library(ggplot2)
```

### Setting working directory

```{r}
here::i_am("Code for Assessing spatial and temporal variability in crop response to bio-based and mineral fertilisers, using remote sensing.qmd") 
```

### Setting theme for plots

```{r}
my_theme <- theme_minimal() + theme_update(
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 16),
        plot.title = element_text(size = 20),
        legend.title = element_text(size = 18),
        legend.text = element_text(size = 16),
        strip.text = element_text(size = 16)
    )
theme_set(my_theme)

# Color palette
# treatment_colors <- c("OG2, Residual fertiliser" = "#1f77b4",
#                      "OG2" = "#ff7f0e",
#                      "Mineral" = "#2ca02c",
#                      "Control" = "#d62728")
# treatment_colors <- c("OG2, Residual fertiliser" = "#1f77b4",  # Blue
#                      "OG2" = "#ff7f0e",  # Orange
#                      "Mineral" = "#2ca02c",  # Green
#                      "Control" = "#d62728")  # Red
treatment_colors <- c(
  "OG2, Residual fertiliser" = "#1f77b4",
  "OG2" = "#ff7f0e",
  "Mineral" = "#2ca02c",
  "Control" = "#d62728",
  "MIN" = "#2ca02c",
                     "CON" = "#d62728",
  "OG2_residual" = "#1f77b4",
  "REF_1" = "#1f77b4",     # Blue
  "REF_2" = "#7f7f7f",     # Gray
  "REF_3" = "#2ca02c",     # Green (original Mineral color)
  "REF_4" = "#9467bd",     # Purple
  "BA6" = "#8c564b",       # Brown
  "BIO" = "#e377c2",       # Pink
  "BVC" = "#bcbd22",       # Olive
  "ECO" = "#17becf",       # Cyan
  "FEK" = "#aec7e8",       # Light blue
  "MO13" = "#ffbb78",      # Light orange
  "PCW" = "#98df8a",       # Light green
  "SDG" = "#ff9896",       # Light red
  "137 kg N/ha*" = "#c5b0d5", # Light purple
  "PAL" = "#c49c94", # Light brown
  "bbf" = "blue",
  "control" = "#d62728",
  "mineral" = "#2ca02c"
)
#Treatment labels largeplot
treatment_labels_lp <- c(  "OG2_residual" = "OG2, Residual fertiliser",
  "OG2" = "OG2",
  "MIN" = "Mineral",
  "CON" = "Control"
)
```

### Defining dates and standards

```{r}
#Dates spring barley (2021)
start_date_sb = as.Date("2021-04-01")
end_date_sb = as.Date("2021-08-25")

#Dates wheat residual
start_date_wwres = as.Date("2021-09-01")
end_date_wwres = as.Date("2022-08-25")

#Dates wheat non residual
start_date_ww = as.Date("2022-03-30")
end_date_ww = as.Date("2022-08-25")

#Alternative dates for "zoom"! 
# #Dates spring barley (2021) 
# start_date_sb = as.Date("2021-05-10")
# end_date_sb = as.Date("2021-07-10")
# 
# #Dates wheat residual
# start_date_wwres = as.Date("2022-05-10")
# end_date_wwres = as.Date("2022-07-10")
# 
# #Dates wheat non residual
# start_date_ww = as.Date("2022-05-10")
# end_date_ww = as.Date("2022-07-10")
```

### Loading data

```{r}
ndre_data25 <- read_csv(here("data", "ndre_data25.csv"))
ndvi_data25 <- read_csv(here("data", "ndvi_data25.csv"))
ndre_data25_uav <- read_csv(here("data", "ndre_uav_field25.csv"))
ndvi_data25_uav <- read_csv(here("data", "ndvi_uav_field25.csv"))
ndvi_data26 <- read_csv(here("data", "ndvi_data26.csv")) 
ndvi_data26_residual <- read_csv(here("data", "ndvi_data26_residual.csv"))
ndre_data26 <- read_csv(here("data", "ndre_data26.csv")) 
ndre_data26_residual <- read_csv(here("data", "ndre_data26_residual.csv"))
ndre_data26 <- read_csv(here("data", "ndre_data26.csv")) 
ndvi_uav_field26 <- read_csv(here("data", "ndvi_uav_field26.csv"))
ndvi_uav_field26_residual <- read_csv(here("data", "ndvi_uav_field26_residual.csv"))
voronoi_withinlargeplots_25 <- read_csv(here("data","voronoi_withinlargeplots_25_2_UAV.csv"))
voronoi_within_smallplot_full_26_nonresdata <- read_csv(here("data","voronoi_within_smallplot_full_26_nonresdata.csv"))
reflectance_soiloptix_largeplot25_satelite <- read_csv(here("data","reflectance_soiloptix_largeplot25_satelite.csv"))

ndvi_uav_field25 <- read_csv(here("data", "ndvi_uav_field25.csv"))
ndre_uav_field25 <- read_csv(here("data", "ndre_uav_field25.csv"))
ndvi_uav_field26 <- read_csv(here("data", "ndvi_uav_field26.csv"))
ndre_uav_field26 <- read_csv(here("data", "ndre_uav_field26.csv"))
ndre_uav_field26_residual <- read_csv(here("data", "ndre_uav_field26_residual.csv"))
ndvi_uav_field26_residual <- read_csv(here("data", "ndvi_uav_field26_residual.csv"))
reflectance_soiloptix_26_satelite <- read_csv(here("data", "reflectance_soiloptix_26.csv"))
reflectance_soiloptix_26_res_sat <- read_csv(here("data", "reflectance_soiloptix_26_res_sat.csv"))
harvest_field25 <- read_csv(here("data", "harvest_field25.csv"))
harvest_field26 <- read_csv(here("data", "harvest_field26.csv"))
ndre_data25_2 <- read_csv(here("data", "ndre_data25_2.csv"))
ndvi_data25_2 <- read_csv(here("data", "ndvi_data25_2.csv"))

```

## Functions for analysis

### Large-plot trial satellite temporal variation and CV

```{r}
lme_analysis_lp <- function(data, response_var, treatment_var = "Treatment", plot_id_var = "PLOT_ID", date_var = "timestamp", start_date, end_date, identifier, plottitle) {
  
  # Find the name of the df
  data_name <- deparse(substitute(data))
  
  # Since we run the code multiple times namin is important
  name_prefix <- paste0(data_name, "_", response_var, "_", identifier)
  
  # Ensuring data is correctly formatted
  data <- transform(data,
                    timestamp = as.Date(data[[date_var]]),
                    Date = ymd(data[[date_var]]),
                    DateFactor = as.factor(data[[date_var]]))
  
  # Recode treatment factor levels
  data[[treatment_var]] <- factor(data[[treatment_var]], 
                                 levels = names(treatment_labels_lp),
                                 labels = treatment_labels_lp)
  
  #Using the dates from above for analysis
  subset_data <- subset(data, timestamp >= start_date & timestamp <= end_date)
  
  #We need a numeric variable for the timedata for the corAR1 argument
  subset_data$timeSinceStart <- as.numeric(subset_data$Date - min(subset_data$Date))
  
  # Identifying variables for analysis 
  fixed_formula <- as.formula(paste(response_var, "~", treatment_var, "*DateFactor"))
  random_formula <- as.formula(paste("~1|", plot_id_var))
  correlation_formula <- as.formula(paste("~timeSinceStart|", plot_id_var))
  
  # Creating and fitting models with and without interaction
  mod_int <- lme(fixed_formula, 
                 random = random_formula, 
                 correlation = corAR1(form = correlation_formula), 
                 data = subset_data, method = "ML")
  
  mod_no_int <- lme(update(fixed_formula, . ~ . - Treatment:DateFactor), 
                    random = random_formula, 
                    correlation = corAR1(form = correlation_formula), 
                    data = subset_data, method = "ML",
                    control = lmeControl(msMaxIter = 2000, msMaxEval = 2000, returnObject=TRUE))
  
  # Comparison of models
  anova_result <- anova(mod_int, mod_no_int)
  
  # Plotting
  #Residualplot no int
  plot1 <- ggplot(subset_data, aes(x = timeSinceStart, 
                                   y = residuals(mod_no_int, type = "normalized"),
                                   col = .data[[treatment_var]])) +
    geom_point() +
    geom_smooth() +
    scale_color_manual(values = treatment_colors) +
    labs(x = "Time since start", y = "Residuals", col = "Treatment", 
         title = paste(name_prefix, "No interaction between Treatment and time,", start_date, "to", end_date))
  
  #Residualplot int
  plot2 <- ggplot(subset_data, aes(x = timeSinceStart, 
                                   y = residuals(mod_int, type = "normalized"),
                                   col = .data[[treatment_var]])) +
    geom_point() +
    geom_smooth() +
    scale_color_manual(values = treatment_colors) +
    labs(x = "Time since start", y = "Residuals", col = "Treatment", 
         title = paste(name_prefix, "Interaction between Treatment and time,", start_date, "to", end_date))
  
  #Mainplot
  plot3 <- ggplot(subset_data, aes(x = Date, 
                                   y = .data[[response_var]],
                                   col = .data[[treatment_var]])) +
    geom_point() +
    geom_smooth(span = 0.4) +
    scale_color_manual(values = treatment_colors) +
    labs(x = "Date", y = response_var, col = "Treatment", 
         title = paste(plottitle))
  
  # Adding QQ plots for both models
  # QQ plot for model without interaction
  plot4 <- ggplot(data.frame(residuals = residuals(mod_no_int, type = "normalized")), 
                  aes(sample = residuals)) +
    stat_qq() +
    stat_qq_line() +
    labs(title = paste(name_prefix, "QQ Plot - Model without interaction"),
         x = "Theoretical Quantiles",
         y = "Sample Quantiles")

  # QQ plot for model with interaction
  plot5 <- ggplot(data.frame(residuals = residuals(mod_int, type = "normalized")), 
                  aes(sample = residuals)) +
    stat_qq() +
    stat_qq_line() +
    labs(title = paste(name_prefix, "QQ Plot - Model with interaction"),
         x = "Theoretical Quantiles",
         y = "Sample Quantiles")
  
  # Creating a list for results
  results <- list(
    model_interaction = mod_int,
    model_no_interaction = mod_no_int,
    anova_result = anova_result,
    plot_residuals_no_int = plot1,
    plot_residuals_int = plot2,
    plot_response = plot3,
    plot_qq_no_int = plot4,
    plot_qq_int = plot5
  )
  
  # Renaming the elements in the list, to distinguish finished or semifinished plots
  names(results) <- c(
    paste0("mod_int_", name_prefix),
    paste0("mod_no_int_", name_prefix),
    paste0("anova_result_", name_prefix),
    paste0("plot_residuals_no_int_", name_prefix),
    paste0("plot_residuals_int_", name_prefix),
    paste0("plot_response_", name_prefix),
    paste0("plot_qq_no_int_", name_prefix),
    paste0("plot_qq_int_", name_prefix)
  )
  
  return(results)
}

```

### Large plot trial - UAV mean and CV

```{r}
lme_analysis_lp_uav <- function(data, response_var, treatment_var = "Treatment", plot_id_var = "PLOT_ID", 
                         date_var = "date", start_date, end_date, identifier, plottitle) {
  
  # Get the name of the data frame
  data_name <- deparse(substitute(data))
  
  # Create a prefix for naming, including the identifier
  name_prefix <- paste0(data_name, "_", response_var, "_", identifier)
  
  # Data preprocessing with explicit NA handling
  data <- data %>%
    mutate(
      timestamp = as.Date(!!sym(date_var)),
      Date = timestamp,
      DateFactor = as.factor(timestamp)
    ) %>%
    # Filter data for date range
    filter(timestamp >= start_date, timestamp <= end_date) %>%
    # Calculate timeSinceStart after filtering
    group_by(!!sym(plot_id_var)) %>%
    mutate(
      timeSinceStart = as.numeric(timestamp - min(timestamp))
    ) %>%
    ungroup() #%>%
  # Create formulas
  fixed_formula <- as.formula(paste(response_var, "~", treatment_var, "*DateFactor"))
  random_formula <- as.formula(paste("~1|", plot_id_var))
  correlation_formula <- as.formula(paste("~timeSinceStart|", plot_id_var))
  
  mod_int <-
    lme(fixed_formula, 
        random = random_formula, 
        correlation = corAR1(form = correlation_formula), 
        data = data, 
        method = "ML",
        na.action = na.omit)
  
    mod_no_int <- lme(update(fixed_formula, . ~ . - Treatment:DateFactor), 
        random = random_formula, 
        correlation = corAR1(form = correlation_formula), 
        data = data, 
        method = "ML",
        na.action = na.omit,
        control = lmeControl(msMaxIter = 2000, msMaxEval = 2000, returnObject=TRUE))
  
  # Create plots with the filtered data
  plot1 <- ggplot(data, aes(x = timeSinceStart, 
                           y = residuals(mod_no_int, type = "normalized"),
                           col = !!sym(treatment_var))) +
    geom_point() +
    geom_smooth() +
    scale_color_manual(values = treatment_colors) +
    labs(x = "Time since start (days)", y = "Residuals", col = "Treatment")
  
  plot2 <- ggplot(data, aes(x = timeSinceStart, 
                           y = residuals(mod_int, type = "normalized"),
                           col = !!sym(treatment_var))) +
    geom_point() +
    geom_smooth() +
    scale_color_manual(values = treatment_colors) +
    labs(x = "Time since start (days)", y = "Residuals", col = "Treatment")
  
  #Finding means
  mean_data <- data %>%
    group_by(Date, !!sym(treatment_var)) %>%
    summarize(
      mean_response = mean(!!sym(response_var), na.rm = TRUE),
      .groups = 'drop'
    )
  
  # Using lines through means instead of smooth
  plot3 <- ggplot() +
    geom_point(data = data, 
              aes(x = Date, 
                  y = !!sym(response_var),
                  color = !!sym(treatment_var))) +
    geom_line(data = mean_data,
             aes(x = Date,
                 y = mean_response,
                 color = !!sym(treatment_var)),
             linewidth = 1) +
    scale_color_manual(values = treatment_colors) +
    labs(x = "Date", y = response_var, col = "Treatment", 
         title = plottitle)
  
  # Adding QQ plots
  plot4 <- ggplot(data.frame(residuals = residuals(mod_no_int, type = "normalized")), 
                  aes(sample = residuals)) +
    stat_qq() +
    stat_qq_line() +
    labs(title = paste(name_prefix, "QQ Plot - Model without interaction"),
         x = "Theoretical Quantiles",
         y = "Sample Quantiles")

  plot5 <- ggplot(data.frame(residuals = residuals(mod_int, type = "normalized")), 
                  aes(sample = residuals)) +
    stat_qq() +
    stat_qq_line() +
    labs(title = paste(name_prefix, "QQ Plot - Model with interaction"),
         x = "Theoretical Quantiles",
         y = "Sample Quantiles")
  
  # Create named list for results
  results <- list(
    model_interaction = mod_int,
    model_no_interaction = mod_no_int,
    anova_result = anova(mod_int, mod_no_int),
    plot_residuals_no_int = plot1,
    plot_residuals_int = plot2,
    plot_response = plot3,
    plot_qq_no_int = plot4,
    plot_qq_int = plot5
  )
  
  # Rename the elements in the list
  names(results) <- c(
    paste0("mod_int_", name_prefix),
    paste0("mod_no_int_", name_prefix),
    paste0("anova_result_", name_prefix),
    paste0("plot_residuals_no_int_", name_prefix),
    paste0("plot_residuals_int_", name_prefix),
    paste0("plot_response_", name_prefix),
    paste0("plot_qq_no_int_", name_prefix),
    paste0("plot_qq_int_", name_prefix)
  )
  
  return(results)
}
```

### Small plot trial sat mean function splitting plot in 3

```{r}
reflectance26_analysis <- function(data, response_var, treatment_var, 
                                   plot_id_var, block_var,
                                   date_var, start_date, end_date, identifier, index) {
  
  # Name DF
  data_name <- deparse(substitute(data))
  
  # Automating naming
  name_prefix <- paste0(data_name, "_", response_var, "_", identifier)
  
  # Transform data
  data <- transform(data,
                    timestamp = as.Date(data[[date_var]]),
                    Date = ymd(data[[date_var]]),
                    DateFactor = as.factor(data[[date_var]]),
                    Treatment = as.factor(data[[treatment_var]]))
  
  data$timeSinceStart <- as.numeric(data$Date - min(data$Date))
   
  # Subset data
  subset_data <- subset(data, timestamp >= start_date & timestamp <= end_date)
  # ## Comment out this part if the model cannot fit and you want to see the plots- from here
  # Create formulas
  fixed_formula_int <- as.formula(paste(response_var, "~", treatment_var, "* DateFactor"))
  fixed_formula_no_int <- as.formula(paste(response_var, "~", treatment_var, "+ DateFactor"))
  random_formula <- as.formula(paste("~ 1 |", block_var, "/", plot_id_var))
  correlation_formula <- as.formula(paste("~ timeSinceStart |", block_var, "/", plot_id_var))

  # Fit models
  mod_int <- lme(fixed_formula_int,
                 random = random_formula,
                 correlation = corAR1(form = correlation_formula),
                 data = subset_data, method = "ML", control = lmeControl(
  maxIter = 1000,
  msMaxIter = 1000,
  opt = "optim",
  tolerance = 1e-4))

  mod_no_int <- lme(fixed_formula_no_int,
                    random = random_formula,
                    correlation = corAR1(form = correlation_formula),
                    data = subset_data, method = "ML", control = lmeControl(
  maxIter = 1000,
  msMaxIter = 1000,
  opt = "optim",
  tolerance = 1e-4))

  # ANOVA comparison
  anova_result <- anova(mod_int, mod_no_int)


  # Plotting
  plot1 <- ggplot(subset_data, aes(x = timeSinceStart,
                                   y = residuals(mod_no_int, type = "normalized"),
                                   col = .data[[treatment_var]])) +
    geom_point() +
    geom_smooth(se=FALSE) +
    scale_color_manual(values = treatment_colors) +
    labs(x = "Time since start", y = "Residuals", col = "Treatment",
         title = paste(name_prefix, "No interaction between Treatment and time,", start_date, "to", end_date))

plot2 <- ggplot(subset_data, aes(x = timeSinceStart,
                                   y = residuals(mod_int, type = "normalized"),
                                   col = .data[[treatment_var]])) +
    geom_point() +
    geom_smooth(se=FALSE) +
    scale_color_manual(values = treatment_colors) +
    labs(x = "Time since start", y = "Residuals", col = "Treatment",
         title = paste(name_prefix, "Interaction between Treatment and time,", start_date, "to", end_date))

  #to here
    # Mean plot with panels and geom_smooth
 
# Create groups for faceting with corrected grouping logic
  subset_data$plot_group <- factor(
    case_when(
      subset_data$Treatment %in% c("REF_1", "REF_2", "REF_3", "REF_4", "137 kg N/ha*") ~ "Reference Treatments",
      subset_data$Treatment %in% c("BA6", "BIO", "BVC", "ECO", "FEK") ~ "BBF Treatments 1",
      subset_data$Treatment %in% c("MO13", "OG2", "PCW", "SDG", "PAL") ~ "BBF Treatments 2",
      TRUE ~ "Other"  
    ),
    levels = c("Reference Treatments", "BBF Treatments 1", "BBF Treatments 2")
  )
# First, create the data subsets
ref_data <- subset_data[subset_data$Treatment %in% c("REF_1", "REF_2", "REF_3", "REF_4", "137 kg N/ha*"), ]
bbf1_data <- subset_data[subset_data$Treatment %in% c("REF_3","BA6", "BIO", "BVC", "ECO", "FEK"), ]
bbf2_data <- subset_data[subset_data$Treatment %in% c("REF_3","MO13", "OG2", "PCW", "SDG", "PAL"), ]

# Create individual plots
plot_ref <- ggplot() +
  geom_smooth(data = ref_data, 
              aes(x = Date, y = .data[[response_var]], 
                  color = Treatment),
              span = 0.4, se = FALSE, alpha = 0.7, size = 0.8) +
  geom_point(data = ref_data,
             aes(x = Date, y = .data[[response_var]], 
                 color = Treatment),
             alpha = 0.4, size = 1) +
  scale_color_manual(values = treatment_colors) +
  scale_y_continuous(
    limits = c(min(subset_data[[response_var]]) * 0.95, 
              max(subset_data[[response_var]]) * 1.05),
    expand = expansion(mult = c(0.02, 0.02))
  ) +
  my_theme +
  labs(x = "Date", 
       y = paste(response_var, index),
       color = "Reference Treatments",
       title = "Reference Treatments")

plot_bbf1 <- ggplot() +
  geom_smooth(data = bbf1_data, 
              aes(x = Date, y = .data[[response_var]], 
                  color = Treatment),
              span = 0.4, se = FALSE, alpha = 0.7, size = 0.8) +
  geom_point(data = bbf1_data,
             aes(x = Date, y = .data[[response_var]], 
                 color = Treatment),
             alpha = 0.4, size = 1) +
  scale_color_manual(values = treatment_colors) +
  scale_y_continuous(
    limits = c(min(subset_data[[response_var]]) * 0.95, 
              max(subset_data[[response_var]]) * 1.05),
    expand = expansion(mult = c(0.02, 0.02))
  ) +
  my_theme+
  labs(x = "Date", 
       y = paste(response_var, index),
       color = "BBF Treatments 1",
       title = "BBF Treatments 1")

plot_bbf2 <- ggplot() +
  geom_smooth(data = bbf2_data, 
              aes(x = Date, y = .data[[response_var]], 
                  color = Treatment),
              span = 0.4, se = FALSE, alpha = 0.7, size = 0.8) +
  geom_point(data = bbf2_data,
             aes(x = Date, y = .data[[response_var]], 
                 color = Treatment),
             alpha = 0.4, size = 1) +
  scale_color_manual(values = treatment_colors) +
  scale_y_continuous(
    limits = c(min(subset_data[[response_var]]) * 0.95, 
              max(subset_data[[response_var]]) * 1.05),
    expand = expansion(mult = c(0.02, 0.02))
  ) +
  my_theme +
  labs(x = "Date", 
       y = paste(response_var, index),
       color = "BBF Treatments 2",
       title = "BBF Treatments 2")

# Combine plots using ggarrange
plot3 <- ggarrange(plot_ref, plot_bbf1, plot_bbf2,
                  ncol = 1,
                  heights = c(1, 1, 1),
                  align = "v",
                  common.legend = FALSE)
 plot4 <- ggplot(data.frame(residuals = residuals(mod_no_int, type = "normalized")), 
                  aes(sample = residuals)) +
    stat_qq() +
    stat_qq_line() +
    labs(title = paste(name_prefix, "QQ Plot - Model without interaction"),
         x = "Theoretical Quantiles",
         y = "Sample Quantiles")

  plot5 <- ggplot(data.frame(residuals = residuals(mod_int, type = "normalized")), 
                  aes(sample = residuals)) +
    stat_qq() +
    stat_qq_line() +
    labs(title = paste(name_prefix, "QQ Plot - Model with interaction"),
         x = "Theoretical Quantiles",
         y = "Sample Quantiles")

  # Update results list to include QQ plots
  results <- list(
    model_interaction = mod_int,
    model_no_interaction = mod_no_int,
    anova_result = anova_result,
    plot_residuals_no_int = plot1,
    plot_residuals_int = plot2,
    plot_response = plot3,
    plot_qq_no_int = plot4,
    plot_qq_int = plot5
  )
  
  # Update names list to include QQ plots
  names(results) <- c(
    paste0("mod_int_", name_prefix),
    paste0("mod_no_int_", name_prefix),
    paste0("anova_result_", name_prefix),
    paste0("plot_residuals_no_int_", name_prefix),
    paste0("plot_residuals_int_", name_prefix),
    paste0("plot_response_", name_prefix),
    paste0("plot_qq_no_int_", name_prefix),
    paste0("plot_qq_int_", name_prefix)
  )
  
  return(results)
}
```

### Small plot trial UAV mean function splitting plot in 3

```{r}
reflectance26_analysis_uav <- function(data, response_var, treatment_var, 
                                   plot_id_var, block_var,
                                   date_var, start_date, end_date, identifier) {
  
  # DF
  data_name <- deparse(substitute(data))
  name_prefix <- paste0(data_name, "_", response_var, "_", identifier)
  
  # Data preprocessing with explicit checks
  data <- data %>%
    mutate(
      timestamp = as.Date(!!sym(date_var)),
      Date = timestamp,
      DateFactor = as.factor(timestamp),
      Treatment = as.factor(!!sym(treatment_var))
    ) %>%
    filter(!is.na(timestamp)) %>%
    filter(timestamp >= start_date & timestamp <= end_date)
  
  # time since start
  data <- data %>%
    group_by(!!sym(plot_id_var)) %>%
    mutate(timeSinceStart = as.numeric(timestamp - min(timestamp))) %>%
    ungroup()
  
  # Subset date range
  subset_data <- subset(data, timestamp >= start_date & timestamp <= end_date)
  
  # Create formulas
  fixed_formula_int <- as.formula(paste(response_var, "~", treatment_var, "* DateFactor"))
  fixed_formula_no_int <- as.formula(paste(response_var, "~", treatment_var, "+ DateFactor"))
  random_formula <- as.formula(paste("~ 1 |", block_var, "/", plot_id_var))
  correlation_formula <- as.formula(paste("~ timeSinceStart |", block_var, "/", plot_id_var))
  
  # Fit models
  mod_int <- lme(fixed_formula_int, 
                 random = random_formula, 
                 correlation = corAR1(form = correlation_formula), 
                 data = subset_data, method = "ML")
  
  mod_no_int <- lme(fixed_formula_no_int, 
                    random = random_formula, 
                    correlation = corAR1(form = correlation_formula), 
                    data = subset_data, method = "ML")
  
  # ANOVA comparison
  anova_result <- anova(mod_int, mod_no_int)
  
  # Plotting with consistent colors
  plot1 <- ggplot(subset_data, aes(x = timeSinceStart, 
                                   y = residuals(mod_no_int, type = "normalized"),
                                   col = .data[[treatment_var]])) +
    geom_point() +
    geom_smooth(se=FALSE) +
    scale_color_manual(values = treatment_colors) +
    labs(x = "Time since start", y = "Residuals", col = "Treatment", 
         title = paste(name_prefix, "No interaction between Treatment and time,", start_date, "to", end_date))
  
  plot2 <- ggplot(subset_data, aes(x = timeSinceStart, 
                                   y = residuals(mod_int, type = "normalized"),
                                   col = .data[[treatment_var]])) +
    geom_point() +
    geom_smooth(se=FALSE) +
    scale_color_manual(values = treatment_colors) +
    labs(x = "Time since start", y = "Residuals", col = "Treatment", 
         title = paste(name_prefix, "Interaction between Treatment and time,", start_date, "to", end_date))
  
  # Create data subsets for plot3
  ref_data <- subset_data[subset_data$Treatment %in% c("REF_1", "REF_2", "REF_3", "REF_4", "137 kg N/ha*"), ]
  bbf1_data <- subset_data[subset_data$Treatment %in% c("REF_3","BA6", "BIO", "BVC", "ECO", "FEK"), ]
  bbf2_data <- subset_data[subset_data$Treatment %in% c("REF_3","MO13", "OG2", "PCW", "SDG", "PAL"), ]
  
  # Calculate means
  ref_means <- ref_data %>%
    group_by(Date, Treatment) %>%
    summarize(
      mean_response = mean(.data[[response_var]], na.rm = TRUE),
      .groups = 'drop'
    )
  
  bbf1_means <- bbf1_data %>%
    group_by(Date, Treatment) %>%
    summarize(
      mean_response = mean(.data[[response_var]], na.rm = TRUE),
      .groups = 'drop'
    )
  
  bbf2_means <- bbf2_data %>%
    group_by(Date, Treatment) %>%
    summarize(
      mean_response = mean(.data[[response_var]], na.rm = TRUE),
      .groups = 'drop'
    )
  
  # plots with points and lines through means
  plot_ref <- ggplot() +
    geom_point(data = ref_data,
               aes(x = Date, y = .data[[response_var]], 
                   color = Treatment),
               alpha = 0.4, size = 1) +
    geom_line(data = ref_means,
              aes(x = Date, y = mean_response, 
                  color = Treatment),
              linewidth = 1) +
    scale_color_manual(values = treatment_colors) +
    scale_y_continuous(
      limits = c(min(subset_data[[response_var]]) * 0.95, 
                max(subset_data[[response_var]]) * 1.05),
      expand = expansion(mult = c(0.02, 0.02))
    ) +
    my_theme +
    labs(x = "Date", 
         y = response_var,
         color = "Reference Treatments",
         title = "Reference Treatments")

  plot_bbf1 <- ggplot() +
    geom_point(data = bbf1_data,
               aes(x = Date, y = .data[[response_var]], 
                   color = Treatment),
               alpha = 0.4, size = 1) +
    geom_line(data = bbf1_means,
              aes(x = Date, y = mean_response, 
                  color = Treatment),
              linewidth = 1) +
    scale_color_manual(values = treatment_colors) +
    scale_y_continuous(
      limits = c(min(subset_data[[response_var]]) * 0.95, 
                max(subset_data[[response_var]]) * 1.05),
      expand = expansion(mult = c(0.02, 0.02))
    ) +
    my_theme +
    labs(x = "Date", 
         y = response_var,
         color = "BBF Treatments 1",
         title = "BBF Treatments 1")

  plot_bbf2 <- ggplot() +
    geom_point(data = bbf2_data,
               aes(x = Date, y = .data[[response_var]], 
                   color = Treatment),
               alpha = 0.4, size = 1) +
    geom_line(data = bbf2_means,
              aes(x = Date, y = mean_response, 
                  color = Treatment),
              linewidth = 1) +
    scale_color_manual(values = treatment_colors) +
    scale_y_continuous(
      limits = c(min(subset_data[[response_var]]) * 0.95, 
                max(subset_data[[response_var]]) * 1.05),
      expand = expansion(mult = c(0.02, 0.02))
    ) +
    my_theme +
    labs(x = "Date", 
         y = response_var,
         color = "BBF Treatments 2",
         title = "BBF Treatments 2")

  # Combine plots using ggarrange
  plot3 <- ggarrange(plot_ref, plot_bbf1, plot_bbf2,
                    ncol = 1,
                    heights = c(1, 1, 1),
                    align = "v",
                    common.legend = FALSE)

  plot4 <- ggplot(data.frame(residuals = residuals(mod_no_int, type = "normalized")), 
                  aes(sample = residuals)) +
    stat_qq() +
    stat_qq_line() +
    labs(title = paste(name_prefix, "QQ Plot - Model without interaction"),
         x = "Theoretical Quantiles",
         y = "Sample Quantiles")

  plot5 <- ggplot(data.frame(residuals = residuals(mod_int, type = "normalized")), 
                  aes(sample = residuals)) +
    stat_qq() +
    stat_qq_line() +
    labs(title = paste(name_prefix, "QQ Plot - Model with interaction"),
         x = "Theoretical Quantiles",
         y = "Sample Quantiles")

  # result list
  results <- list(
    model_interaction = mod_int,
    model_no_interaction = mod_no_int,
    anova_result = anova_result,
    plot_residuals_no_int = plot1,
    plot_residuals_int = plot2,
    plot_response = plot3,
    plot_qq_no_int = plot4,
    plot_qq_int = plot5
  )
  
  # adding names
  names(results) <- c(
    paste0("mod_int_", name_prefix),
    paste0("mod_no_int_", name_prefix),
    paste0("anova_result_", name_prefix),
    paste0("plot_residuals_no_int_", name_prefix),
    paste0("plot_residuals_int_", name_prefix),
    paste0("plot_response_", name_prefix),
    paste0("plot_qq_no_int_", name_prefix),
    paste0("plot_qq_int_", name_prefix)
  )
  
  return(results)
}
```

### Function for comparing aggregated fertilisers to individual levels - satellite data

```{r}
reflectance26_analysis_aggregated <- function(data, response_var, treatment_var, treatment_var_aggregated, 
                                   plot_id_var, block_var,
                                   date_var, start_date, end_date, identifier, index) {
  
  # DF
  data_name <- deparse(substitute(data))
  
  # Naming
  name_prefix <- paste0(data_name, "_", response_var, "_", identifier)
  
  # Data preprocessing
  data <- transform(data,
                    timestamp = as.Date(data[[date_var]]),
                    Date = ymd(data[[date_var]]),
                    DateFactor = as.factor(data[[date_var]]),
                    Treatment = as.factor(data[[treatment_var]]))
  
  data$timeSinceStart <- as.numeric(data$Date - min(data$Date))
  
  # Subset data
  subset_data <- subset(data, timestamp >= start_date & timestamp <= end_date)
  
  # Create formulas
  fixed_formula_int <- as.formula(paste(response_var, "~", treatment_var, "* DateFactor"))
  fixed_formula_aggregated_int <- as.formula(paste(response_var, "~", treatment_var_aggregated, "* DateFactor"))
  random_formula <- as.formula(paste("~ 1 |", block_var, "/", plot_id_var))
  correlation_formula <- as.formula(paste("~ timeSinceStart |", block_var, "/", plot_id_var))
  
  # Fit models
  mod_int <- lme(fixed_formula_int, 
                 random = random_formula, 
                 correlation = corAR1(form = correlation_formula), 
                 data = subset_data, method = "ML")
  
  mod_aggregated_int <- lme(fixed_formula_aggregated_int, 
                    random = random_formula, 
                    correlation = corAR1(form = correlation_formula), 
                    data = subset_data, method = "ML")
  
  # ANOVA comparison
  anova_result <- anova(mod_int, mod_aggregated_int)
  
  # Plotting
  plot1 <- ggplot(subset_data, aes(x = timeSinceStart, 
                                   y = residuals(mod_aggregated_int, type = "normalized"),
                                   col = .data[[treatment_var]])) +
    geom_point() +
    geom_smooth() +
    scale_color_manual(values = treatment_colors) +
    labs(x = "Time since start", y = "Residuals", col = "Treatment", 
         title = paste(name_prefix, "No interaction between Treatment and time,", start_date, "to", end_date))
  
  plot2 <- ggplot(subset_data, aes(x = timeSinceStart, 
                                   y = residuals(mod_int, type = "normalized"),
                                   col = .data[[treatment_var]])) +
    geom_point() +
    geom_smooth() +
    scale_color_manual(values = treatment_colors) +
    labs(x = "Time since start", y = "Residuals", col = "Treatment", 
         title = paste(name_prefix, "Interaction between Treatment and time,", start_date, "to", end_date))
  
 plot4 <- ggplot(data.frame(residuals = residuals(mod_aggregated_int, type = "normalized")), 
                  aes(sample = residuals)) +
    stat_qq() +
    stat_qq_line() +
    labs(title = paste(name_prefix, "QQ Plot - Model with aggregated treatments"),
         x = "Theoretical Quantiles",
         y = "Sample Quantiles")

  plot5 <- ggplot(data.frame(residuals = residuals(mod_int, type = "normalized")), 
                  aes(sample = residuals)) +
    stat_qq() +
    stat_qq_line() +
    labs(title = paste(name_prefix, "QQ Plot - Model with individual treatments"),
         x = "Theoretical Quantiles",
         y = "Sample Quantiles")

  # Update results list to include QQ plots
  results <- list(
    model_interaction = mod_int,
    model_no_interaction = mod_aggregated_int,
    anova_result = anova_result,
    plot_residuals_no_int = plot1,
    plot_residuals_int = plot2,
    plot_qq_aggregated = plot4,
    plot_qq_individual = plot5
  )
  
  # Update names list to include QQ plots
  names(results) <- c(
    paste0("mod_int_", name_prefix),
    paste0("mod_no_int_", name_prefix),
    paste0("anova_result_", name_prefix),
    paste0("plot_residuals_no_int_", name_prefix),
    paste0("plot_residuals_int_", name_prefix),
    paste0("plot_qq_aggregated_", name_prefix),
    paste0("plot_qq_individual_", name_prefix)
  )
  
  return(results)
}
```

## Running functions

#### Mean NDRE sat large-plot trial

```{r}
# Run analysis for spring barley (2021)
results_ndre_data25_mean_sb <- lme_analysis_lp(ndre_data25, 
                           response_var = "mean", 
                           treatment_var = "Treatment",
                           plot_id_var = "PLOT_ID",
                           date_var = "timestamp",
                           start_date = start_date_sb, 
                           end_date = end_date_sb,
                           identifier = "sb" ,
                           plottitle = "NDRE over time, large-plot trial - Spring Barley - 2021")

# Access results with new names
print(results_ndre_data25_mean_sb$anova_result_ndre_data25_mean_sb)

# Display plots with new names
print(results_ndre_data25_mean_sb$plot_residuals_no_int_ndre_data25_mean_sb)
print(results_ndre_data25_mean_sb$plot_residuals_int_ndre_data25_mean_sb)
print(results_ndre_data25_mean_sb$plot_response_ndre_data25_mean_sb)
print(results_ndre_data25_mean_sb$plot_qq_no_int_ndre_data25_mean_sb)
print(results_ndre_data25_mean_sb$plot_qq_int_ndre_data25_mean_sb)

# Analysis for spring Winter wheat (2022)
results_ndre_data25_mean_ww <- lme_analysis_lp(ndre_data25, 
                           response_var = "mean", 
                           treatment_var = "Treatment",
                           plot_id_var = "PLOT_ID",
                           date_var = "timestamp",
                           start_date = start_date_ww, 
                           end_date = end_date_ww,
                           identifier = "ww",
                           plottitle = "NDRE over time, large-plot trial - Winter Wheat - 2022")

# Access results with new names
print(results_ndre_data25_mean_ww$anova_result_ndre_data25_mean_ww)

# Show plots
print(results_ndre_data25_mean_ww$plot_residuals_no_int_ndre_data25_mean_ww)
print(results_ndre_data25_mean_ww$plot_residuals_int_ndre_data25_mean_ww)
print(results_ndre_data25_mean_ww$plot_response_ndre_data25_mean_ww)
print(results_ndre_data25_mean_ww$plot_qq_no_int_ndre_data25_mean_ww)
print(results_ndre_data25_mean_ww$plot_qq_int_ndre_data25_mean_ww)

```

#### Mean NDVI sat largeplot trial

```{r}
# Run analysis for spring barley (2021)
results_ndvi_data25_mean_sb <- lme_analysis_lp(ndvi_data25, 
                           response_var = "mean", 
                           treatment_var = "Treatment",
                           plot_id_var = "PLOT_ID",
                           date_var = "timestamp",
                           start_date = start_date_sb, 
                           end_date = end_date_sb,
                           identifier = "sb",
                           plottitle = "NDVI over time, large-plot trial - Spring Barley - 2021")

# Access results with new names
print(results_ndvi_data25_mean_sb$anova_result_ndvi_data25_mean_sb)

# Display plots with new names
print(results_ndvi_data25_mean_sb$plot_residuals_no_int_ndvi_data25_mean_sb)
print(results_ndvi_data25_mean_sb$plot_residuals_int_ndvi_data25_mean_sb)
print(results_ndvi_data25_mean_sb$plot_response_ndvi_data25_mean_sb)
print(results_ndvi_data25_mean_sb$plot_qq_no_int_ndvi_data25_mean_sb)
print(results_ndvi_data25_mean_sb$plot_qq_int_ndvi_data25_mean_sb)


# Run analysis for spring Winter wheat (2022)
results_ndvi_data25_mean_ww <- lme_analysis_lp(ndvi_data25, 
                           response_var = "mean", 
                           treatment_var = "Treatment",
                           plot_id_var = "PLOT_ID",
                           date_var = "timestamp",
                           start_date = start_date_ww, 
                           end_date = end_date_ww,
                           identifier = "ww",
                           plottitle = "NDVI over time, large-plot trial - Winter Wheat - 2022")

# Access results with new names
print(results_ndvi_data25_mean_ww$anova_result_ndvi_data25_mean_ww)

# Display plots with new names
print(results_ndvi_data25_mean_ww$plot_residuals_no_int_ndvi_data25_mean_ww)
print(results_ndvi_data25_mean_ww$plot_residuals_int_ndvi_data25_mean_ww)
print(results_ndvi_data25_mean_ww$plot_response_ndvi_data25_mean_ww)
print(results_ndvi_data25_mean_ww$plot_qq_no_int_ndvi_data25_mean_ww)
print(results_ndvi_data25_mean_ww$plot_qq_int_ndvi_data25_mean_ww)
```

#### Mean NDRE UAV largeplot trial

```{r}
# Convert the numeric dates to Date format and recode treatments
ndre_data25_uav <- ndre_data25_uav %>%
  mutate(
    date = as.Date(as.character(date), format = "%Y%m%d"),
    Treatment = case_when(
      T_2022 == "Mineral N 2022" ~ "Mineral",
      T_2022 == "OG2 andet 2022" ~ "OG2, Residual fertiliser",
      T_2022 == "OG2 2022" ~ "OG2",
      T_2022 == "Kontrol 2022" ~ "Control",
      TRUE ~ T_2022
    ),
    Treatment = factor(Treatment,
                    levels = c("OG2, Residual fertiliser",
                             "OG2",
                             "Mineral",
                             "Control"))
  )

# Run analysis
results_ndre_data25_uav_mean_ww <- lme_analysis_lp_uav(ndre_data25_uav,
                           response_var = "mean",
                           treatment_var = "Treatment",
                           plot_id_var = "PLOT_ID",
                           date_var = "date",
                           start_date = start_date_ww,
                           end_date = end_date_ww,
                           identifier = "ww",
                           plottitle = "Mean NDRE over time, large plot trial, Winter Wheat, 2022")



print(results_ndre_data25_uav_mean_ww$plot_residuals_no_int_ndre_data25_uav_mean_ww)
print(results_ndre_data25_uav_mean_ww$plot_residuals_int_ndre_data25_uav_mean_ww)
print(results_ndre_data25_uav_mean_ww$plot_response_ndre_data25_uav_mean_ww)
print(results_ndre_data25_uav_mean_ww$plot_qq_no_int_ndre_data25_uav_mean_ww)
print(results_ndre_data25_uav_mean_ww$plot_qq_int_ndre_data25_uav_mean_ww)

# ANOVA results
print(results_ndre_data25_uav_mean_ww$anova_result_ndre_data25_uav_mean_ww)
```

#### Mean NDVI UAV largeplot trial

```{r}
ndvi_data25_uav <- ndvi_data25_uav %>%
  mutate(
    date = as.Date(as.character(date), format = "%Y%m%d"),
    Treatment = case_when(
      T_2022 == "Mineral N 2022" ~ "Mineral",
      T_2022 == "OG2 andet 2022" ~ "OG2, Residual fertiliser",
      T_2022 == "OG2 2022" ~ "OG2",
      T_2022 == "Kontrol 2022" ~ "Control",
      TRUE ~ T_2022
    ),
    Treatment = factor(Treatment, 
                    levels = c("OG2, Residual fertiliser", 
                             "OG2", 
                             "Mineral", 
                             "Control"))
  )

# Run analysis
results_ndvi_data25_uav_mean_ww <- lme_analysis_lp_uav(ndvi_data25_uav, 
                           response_var = "mean", 
                           treatment_var = "Treatment",
                           plot_id_var = "PLOT_ID",
                           date_var = "date",
                           start_date = start_date_ww, 
                           end_date = end_date_ww,
                           identifier = "ww",
                           plottitle = "Mean NDVI over time, large-plot trial, Winter Wheat, 2022")



# Print
print(results_ndvi_data25_uav_mean_ww$plot_residuals_no_int_ndvi_data25_uav_mean_ww)
print(results_ndvi_data25_uav_mean_ww$plot_residuals_int_ndvi_data25_uav_mean_ww)
print(results_ndvi_data25_uav_mean_ww$plot_response_ndvi_data25_uav_mean_ww)
print(results_ndvi_data25_uav_mean_ww$plot_qq_no_int_ndvi_data25_uav_mean_ww)
print(results_ndvi_data25_uav_mean_ww$plot_qq_int_ndvi_data25_uav_mean_ww)

# ANOVA results
print(results_ndvi_data25_uav_mean_ww$anova_result_ndvi_data25_uav_mean_ww)
```

#### Mean NDRE sat small plot trial

```{r}
# Analysis for spring barley (2021)
results_ndre_data26_mean_sb <- reflectance26_analysis(ndre_data26, 
                                             response_var = "mean", 
                                             treatment_var = "Treatment",
                                             plot_id_var = "PLOT_ID",
                                             block_var = "Block_a",
                                             date_var = "timestamp",
                                             start_date = start_date_sb, 
                                             end_date = end_date_sb,
                                             identifier = "sb",
                                             index = "NDRE")

# Results with new names
print(results_ndre_data26_mean_sb$anova_result_ndre_data26_mean_sb)


# Plots with new names
print(results_ndre_data26_mean_sb$plot_residuals_no_int_ndre_data26_mean_sb)
print(results_ndre_data26_mean_sb$plot_residuals_int_ndre_data26_mean_sb)
print(results_ndre_data26_mean_sb$plot_response_ndre_data26_mean_sb)
print(results_ndre_data26_mean_sb$plot_qq_no_int_ndre_data26_mean_sb)
print(results_ndre_data26_mean_sb$plot_qq_int_ndre_data26_mean_sb)

## Winter wheat results

results_ndre_data26_mean_ww <- reflectance26_analysis(ndre_data26, 
                                             response_var = "mean", 
                                             treatment_var = "Treatment",
                                             plot_id_var = "PLOT_ID",
                                             block_var = "Block_a",
                                             date_var = "timestamp",
                                             start_date = start_date_ww, 
                                             end_date = end_date_ww,
                                             identifier = "ww", 
                                             index = "NDRE")


# Access results for winter wheat
print(results_ndre_data26_mean_ww$anova_result_ndre_data26_mean_ww)
print(results_ndre_data26_mean_ww$plot_residuals_no_int_ndre_data26_mean_ww)
print(results_ndre_data26_mean_ww$plot_residuals_int_ndre_data26_mean_ww)
print(results_ndre_data26_mean_ww$plot_response_ndre_data26_mean_ww)
print(results_ndre_data26_mean_ww$plot_qq_no_int_ndre_data26_mean_ww)
print(results_ndre_data26_mean_ww$plot_qq_int_ndre_data26_mean_ww)

# Run analysis for residual fertilised plot
#### Not able to run this part due to "False convergence". The plot can be made if the function is run again with the model section commented out. 
# results_ndre_data26_residual_mean_ww <- reflectance26_analysis(ndre_data26_residual,
#                                              response_var = "mean",
#                                              treatment_var = "Treatment",
#                                              plot_id_var = "PLOT_ID",
#                                              block_var = "Block_a",
#                                              date_var = "timestamp",
#                                              start_date = start_date_wwres,
#                                              end_date = end_date_wwres,
#                                              identifier = "ww",
#                                              index = "ndre")


# Access results with new names
# print(results_ndre_data26_residual_mean_ww$anova_result_ndre_data26_residual_mean_ww)
# 
# # Display plots with new names
# print(results_ndre_data26_residual_mean_ww$plot_residuals_no_int_ndre_data26_residual_mean_ww)
# print(results_ndre_data26_residual_mean_ww$plot_residuals_int_ndre_data26_residual_mean_ww)
# print(results_ndre_data26_residual_mean_ww$plot_response_ndre_data26_residual_mean_ww)
```

#### Mean NDVI sat small plot trial

```{r}
#Spring barley analysis
results_ndvi_data26_mean_sb <- reflectance26_analysis(ndvi_data26, 
                                             response_var = "mean", 
                                             treatment_var = "Treatment",
                                             plot_id_var = "PLOT_ID",
                                             block_var = "Block_a",
                                             date_var = "timestamp",
                                             start_date = start_date_sb, 
                                             end_date = end_date_sb,
                                             identifier = "sb",
                                             index ="NDVI")

# Access results
print(results_ndvi_data26_mean_sb$anova_result_ndvi_data26_mean_sb)

# Display plots
print(results_ndvi_data26_mean_sb$plot_residuals_no_int_ndvi_data26_mean_sb)
print(results_ndvi_data26_mean_sb$plot_residuals_int_ndvi_data26_mean_sb)
print(results_ndvi_data26_mean_sb$plot_response_ndvi_data26_mean_sb)
print(results_ndvi_data26_mean_sb$plot_qq_no_int_ndvi_data26_mean_sb)
print(results_ndvi_data26_mean_sb$plot_qq_int_ndvi_data26_mean_sb)

# Winter wheat results
results_ndvi_data26_mean_ww <- reflectance26_analysis(ndvi_data26, 
                                             response_var = "mean", 
                                             treatment_var = "Treatment",
                                             plot_id_var = "PLOT_ID",
                                             block_var = "Block_a",
                                             date_var = "timestamp",
                                             start_date = start_date_ww, 
                                             end_date = end_date_ww,
                                             identifier = "ww",
                                             index= "NDVI")

#results for winter wheat
print(results_ndvi_data26_mean_ww$anova_result_ndvi_data26_mean_ww)
print(results_ndvi_data26_mean_ww$plot_residuals_no_int_ndvi_data26_mean_ww)
print(results_ndvi_data26_mean_ww$plot_residuals_int_ndvi_data26_mean_ww)
print(results_ndvi_data26_mean_ww$plot_response_ndvi_data26_mean_ww)
print(results_ndvi_data26_mean_ww$plot_qq_no_int_ndvi_data26_mean_ww)
print(results_ndvi_data26_mean_ww$plot_qq_int_ndvi_data26_mean_ww)


# analysis for residual fertilised plot
results_ndvi_data26_residual_mean_ww <- reflectance26_analysis(ndvi_data26_residual, 
                                             response_var = "mean", 
                                             treatment_var = "Treatment",
                                             plot_id_var = "PLOT_ID",
                                             block_var = "Block_a",
                                             date_var = "timestamp",
                                             start_date = start_date_wwres, 
                                             end_date = end_date_wwres,
                                             identifier = "ww",
                                             index = "NDVI")

results_ndvi_data26_residual_mean_ww$plot_response_ndvi_data26_residual_mean_ww <- 
  annotate_figure(results_ndvi_data26_residual_mean_ww$plot_response_ndvi_data26_residual_mean_ww,
                 top = text_grob("NDVI over time, Small plot trial - Winter Wheat, residual fertiliser - 2022",
                               face = "bold", size = 14))

# Access results with new names
print(results_ndvi_data26_residual_mean_ww$anova_result_ndvi_data26_residual_mean_ww)

# Display plots with new names
print(results_ndvi_data26_residual_mean_ww$plot_residuals_no_int_ndvi_data26_residual_mean_ww)
print(results_ndvi_data26_residual_mean_ww$plot_residuals_int_ndvi_data26_residual_mean_ww)
print(results_ndvi_data26_residual_mean_ww$plot_response_ndvi_data26_residual_mean_ww)
print(results_ndvi_data26_residual_mean_ww$plot_qq_no_int_ndvi_data26_residual_mean_ww)
print(results_ndvi_data26_residual_mean_ww$plot_qq_int_ndvi_data26_residual_mean_ww)
```

#### Mean NDVI smallplot UAV

```{r}
ndvi_uav_field26 <- read_csv(here("data", "ndvi_uav_field26.csv"))
ndvi_uav_field26_residual <- read_csv(here("data", "ndvi_uav_field26_residual.csv"))


ndvi_uav_field26 <- ndvi_uav_field26 %>%
  mutate(
    # Convert numeric date directly to character then to Date
    date = as.Date(sprintf("%08d", date), format = "%Y%m%d"),
    Treatment = Treatment_2022,
    Treatment = factor(Treatment)
  )

# Run analysis
results_ndvi_field26_mean_ww <- reflectance26_analysis_uav(ndvi_uav_field26, 
                                             response_var = "mean", 
                                             treatment_var = "Treatment",
                                             plot_id_var = "PLOT_ID",
                                             block_var = "Block_a",
                                             date_var = "date",
                                             start_date = start_date_ww, 
                                             end_date = end_date_ww,
                                             identifier = "ww")


# RESIDUAL 

# Process data with simpler date conversion
ndvi_uav_field26_residual <- ndvi_uav_field26_residual %>%
  mutate(
    # Convert numeric date directly to character then to Date
    date = as.Date(sprintf("%08d", date), format = "%Y%m%d"),
    Treatment = Treatment_2022,
    Treatment = factor(Treatment)
  )

# Run analysis
results_ndvi_field26_mean_ww_residual <- reflectance26_analysis_uav(ndvi_uav_field26_residual, 
                                             response_var = "mean", 
                                             treatment_var = "Treatment",
                                             plot_id_var = "PLOT_ID",
                                             block_var = "Block_a",
                                             date_var = "date",
                                             start_date = start_date_ww, 
                                             end_date = end_date_ww,
                                             identifier = "ww")
# For regular UAV analysis
print(results_ndvi_field26_mean_ww$plot_response_ndvi_uav_field26_mean_ww)
print(results_ndvi_field26_mean_ww$plot_residuals_no_int_ndvi_uav_field26_mean_ww)
print(results_ndvi_field26_mean_ww$plot_residuals_int_ndvi_uav_field26_mean_ww)
print(results_ndvi_field26_mean_ww$anova_result_ndvi_uav_field26_mean_ww)
print(results_ndvi_field26_mean_ww$plot_qq_no_int_ndvi_uav_field26_mean_ww)
print(results_ndvi_field26_mean_ww$plot_qq_int_ndvi_uav_field26_mean_ww)

# For residual UAV analysis
print(results_ndvi_field26_mean_ww_residual$plot_response_ndvi_uav_field26_residual_mean_ww)
print(results_ndvi_field26_mean_ww_residual$plot_residuals_no_int_ndvi_uav_field26_residual_mean_ww)
print(results_ndvi_field26_mean_ww_residual$plot_residuals_int_ndvi_uav_field26_residual_mean_ww)
print(results_ndvi_field26_mean_ww_residual$anova_result_ndvi_uav_field26_residual_mean_ww)
print(results_ndvi_field26_mean_ww_residual$plot_qq_no_int_ndvi_uav_field26_residual_mean_ww)
print(results_ndvi_field26_mean_ww_residual$plot_qq_int_ndvi_uav_field26_residual_mean_ww)
```

#### NDRE small plot UAV

```{r}
# Read data
ndre_uav_field26 <- read_csv(here("data", "ndre_uav_field26.csv"))
ndre_uav_field26_residual <- read_csv(here("data", "ndre_uav_field26_residual.csv"))

ndre_uav_field26 <- ndre_uav_field26 %>%
  mutate(
    # Convert numeric date directly to character then to Date
    date = as.Date(sprintf("%08d", date), format = "%Y%m%d"),
    Treatment = Treatment_2022,
    Treatment = factor(Treatment)
  )

# Run analysis
results_ndre_field26_mean_ww <- reflectance26_analysis_uav(ndre_uav_field26, 
                                             response_var = "mean", 
                                             treatment_var = "Treatment",
                                             plot_id_var = "PLOT_ID",
                                             block_var = "Block_a",
                                             date_var = "date",
                                             start_date = start_date_ww, 
                                             end_date = end_date_ww,
                                             identifier = "ww")

# RESIDUAL 
# Process data with simpler date conversion
ndre_uav_field26_residual <- ndre_uav_field26_residual %>%
  mutate(
    # Convert numeric date directly to character then to Date
    date = as.Date(sprintf("%08d", date), format = "%Y%m%d"),
    Treatment = Treatment_2022,
    Treatment = factor(Treatment)
  )

# Run analysis
results_ndre_field26_mean_ww_residual <- reflectance26_analysis_uav(ndre_uav_field26_residual, 
                                             response_var = "mean", 
                                             treatment_var = "Treatment",
                                             plot_id_var = "PLOT_ID",
                                             block_var = "Block_a",
                                             date_var = "date",
                                             start_date = start_date_ww, 
                                             end_date = end_date_ww,
                                             identifier = "ww")

# For regular UAV analysis
print(results_ndre_field26_mean_ww$plot_response_ndre_uav_field26_mean_ww)
print(results_ndre_field26_mean_ww$plot_residuals_no_int_ndre_uav_field26_mean_ww)
print(results_ndre_field26_mean_ww$plot_residuals_int_ndre_uav_field26_mean_ww)
print(results_ndre_field26_mean_ww$anova_result_ndre_uav_field26_mean_ww)
print(results_ndre_field26_mean_ww$plot_qq_no_int_ndre_uav_field26_mean_ww)
print(results_ndre_field26_mean_ww$plot_qq_int_ndre_uav_field26_mean_ww)

# For residual UAV analysis
print(results_ndre_field26_mean_ww_residual$plot_response_ndre_uav_field26_residual_mean_ww)
print(results_ndre_field26_mean_ww_residual$plot_residuals_no_int_ndre_uav_field26_residual_mean_ww)
print(results_ndre_field26_mean_ww_residual$plot_residuals_int_ndre_uav_field26_residual_mean_ww)
print(results_ndre_field26_mean_ww_residual$anova_result_ndre_uav_field26_residual_mean_ww)
print(results_ndre_field26_mean_ww_residual$plot_qq_no_int_ndre_uav_field26_residual_mean_ww)
print(results_ndre_field26_mean_ww_residual$plot_qq_int_ndre_uav_field26_residual_mean_ww)
```

## Comparing all fertilisers aggregated to analysing each fertiliser

#### NDVI

```{r}
# Run analysis for spring barley (2021)
results_ndvi_data26_mean_sb_agg <- reflectance26_analysis_aggregated(ndvi_data26, 
                                             response_var = "mean", 
                                             treatment_var = "Treatment_2021",
                                             treatment_var_aggregated = "fertiliser_type",
                                             plot_id_var = "PLOT_ID",
                                             block_var = "Block_a",
                                             date_var = "timestamp",
                                             start_date = start_date_sb, 
                                             end_date = end_date_sb,
                                             identifier = "sb",
                                             index = "NDVI")


## Winter wheat results

results_ndvi_data26_mean_ww_agg <- reflectance26_analysis_aggregated(ndvi_data26, 
                                             response_var = "mean", 
                                             treatment_var = "Treatment_2022",
                                             treatment_var_aggregated = "fertiliser_type",
                                             plot_id_var = "PLOT_ID",
                                             block_var = "Block_a",
                                             date_var = "timestamp",
                                             start_date = start_date_ww, 
                                             end_date = end_date_ww,
                                             identifier = "ww",
                                             index = "NDVI"
                                             )



# Run analysis for spring barley (2021)
results_ndvi_data26_residual_mean_ww_agg <- reflectance26_analysis_aggregated(ndvi_data26_residual, 
                                             response_var = "mean", 
                                             treatment_var = "Treatment_2022",
                                             treatment_var_aggregated = "fertiliser_type",
                                             plot_id_var = "PLOT_ID",
                                             block_var = "Block_a",
                                             date_var = "timestamp",
                                             start_date = start_date_wwres, 
                                             end_date = end_date_wwres,
                                             identifier = "ww", 
                                             index= "NDVI")

# Spring Barley prints
print(results_ndvi_data26_mean_sb_agg$anova_result_ndvi_data26_mean_sb)
print(results_ndvi_data26_mean_sb_agg$plot_residuals_no_int_ndvi_data26_mean_sb)
print(results_ndvi_data26_mean_sb_agg$plot_residuals_int_ndvi_data26_mean_sb)
print(results_ndvi_data26_mean_sb_agg$plot_qq_aggregated_ndvi_data26_mean_sb)
print(results_ndvi_data26_mean_sb_agg$plot_qq_individual_ndvi_data26_mean_sb)

# Winter Wheat prints
print(results_ndvi_data26_mean_ww_agg$anova_result_ndvi_data26_mean_ww)
print(results_ndvi_data26_mean_ww_agg$plot_residuals_no_int_ndvi_data26_mean_ww)
print(results_ndvi_data26_mean_ww_agg$plot_residuals_int_ndvi_data26_mean_ww)
print(results_ndvi_data26_mean_ww_agg$plot_qq_aggregated_ndvi_data26_mean_ww)
print(results_ndvi_data26_mean_ww_agg$plot_qq_individual_ndvi_data26_mean_ww)

# Residual analysis prints
print(results_ndvi_data26_residual_mean_ww_agg$anova_result_ndvi_data26_residual_mean_ww)
print(results_ndvi_data26_residual_mean_ww_agg$plot_residuals_no_int_ndvi_data26_residual_mean_ww)
print(results_ndvi_data26_residual_mean_ww_agg$plot_residuals_int_ndvi_data26_residual_mean_ww)
print(results_ndvi_data26_residual_mean_ww_agg$plot_qq_aggregated_ndvi_data26_residual_mean_ww)
print(results_ndvi_data26_residual_mean_ww_agg$plot_qq_individual_ndvi_data26_residual_mean_ww)
print(results_ndvi_data26_mean_sb)
```

#### NDRE

```{r}
# Analysis for spring barley (2021)
results_ndre_data26_mean_sb_agg <- reflectance26_analysis_aggregated(ndre_data26, 
                                             response_var = "mean", 
                                             treatment_var = "Treatment_2021",
                                             treatment_var_aggregated = "fertiliser_type",
                                             plot_id_var = "PLOT_ID",
                                             block_var = "Block_a",
                                             date_var = "timestamp",
                                             start_date = start_date_sb, 
                                             end_date = end_date_sb,
                                             identifier = "sb",
                                             index = "NDRE")
## Winter wheat results
results_ndre_data26_mean_ww_agg <- reflectance26_analysis_aggregated(ndre_data26, 
                                             response_var = "mean", 
                                             treatment_var = "Treatment_2022",
                                             treatment_var_aggregated = "fertiliser_type",
                                             plot_id_var = "PLOT_ID",
                                             block_var = "Block_a",
                                             date_var = "timestamp",
                                             start_date = start_date_ww, 
                                             end_date = end_date_ww,
                                             identifier = "ww",
                                             index = "NDRE"
                                             )
# Analysis for residual
results_ndre_data26_residual_mean_ww_agg <- reflectance26_analysis_aggregated(ndre_data26_residual, 
                                             response_var = "mean", 
                                             treatment_var = "Treatment_2022",
                                             treatment_var_aggregated = "fertiliser_type",
                                             plot_id_var = "PLOT_ID",
                                             block_var = "Block_a",
                                             date_var = "timestamp",
                                             start_date = start_date_wwres, 
                                             end_date = end_date_wwres,
                                             identifier = "ww", 
                                             index= "NDRE")
# Spring Barley prints
print(results_ndre_data26_mean_sb_agg$anova_result_ndre_data26_mean_sb)
print(results_ndre_data26_mean_sb_agg$plot_residuals_no_int_ndre_data26_mean_sb)
print(results_ndre_data26_mean_sb_agg$plot_residuals_int_ndre_data26_mean_sb)
print(results_ndre_data26_mean_sb_agg$plot_qq_aggregated_ndre_data26_mean_sb)
print(results_ndre_data26_mean_sb_agg$plot_qq_individual_ndre_data26_mean_sb)

# Winter Wheat prints
print(results_ndre_data26_mean_ww_agg$anova_result_ndre_data26_mean_ww)
print(results_ndre_data26_mean_ww_agg$plot_residuals_no_int_ndre_data26_mean_ww)
print(results_ndre_data26_mean_ww_agg$plot_residuals_int_ndre_data26_mean_ww)
print(results_ndre_data26_mean_ww_agg$plot_qq_aggregated_ndre_data26_mean_ww)
print(results_ndre_data26_mean_ww_agg$plot_qq_individual_ndre_data26_mean_ww)

# Residual analysis prints
print(results_ndre_data26_residual_mean_ww_agg$anova_result_ndre_data26_residual_mean_ww)
print(results_ndre_data26_residual_mean_ww_agg$plot_residuals_int_ndre_data26_residual_mean_ww)
print(results_ndre_data26_residual_mean_ww_agg$plot_qq_aggregated_ndre_data26_residual_mean_ww)
print(results_ndre_data26_residual_mean_ww_agg$plot_qq_individual_ndre_data26_residual_mean_ww)
```

## CV

#### CV NDRE sat Large-plot trial

```{r}
ndre_data25$cv <- (ndre_data25$std / ndre_data25$mean)

# Run analysis for spring barley (2021)
results_ndre_data25_cv_sb <- lme_analysis_lp(ndre_data25, 
                           response_var = "cv", 
                           treatment_var = "Treatment",
                           plot_id_var = "PLOT_ID",
                           date_var = "timestamp",
                           start_date = start_date_sb, 
                           end_date = end_date_sb,
                           identifier = "sb",
                           plottitle = "CV over time, NDRE, field 25 - Spring Barley - 2022")

# Access results with new names
print(results_ndre_data25_cv_sb$anova_result_ndre_data25_cv_sb)

# Display plots with new names
print(results_ndre_data25_cv_sb$plot_residuals_no_int_ndre_data25_cv_sb)
print(results_ndre_data25_cv_sb$plot_residuals_int_ndre_data25_cv_sb)
print(results_ndre_data25_cv_sb$plot_response_ndre_data25_cv_sb)
print(results_ndre_data25_cv_sb$plot_qq_no_int_ndre_data25_cv_sb)
print(results_ndre_data25_cv_sb$plot_qq_int_ndre_data25_cv_sb)


# Run analysis for spring Winter wheat (2022)
results_ndre_data25_cv_ww <- lme_analysis_lp(ndre_data25, 
                           response_var = "cv", 
                           treatment_var = "Treatment",
                           plot_id_var = "PLOT_ID",
                           date_var = "timestamp",
                           start_date = start_date_ww, 
                           end_date = end_date_ww,
                           identifier = "ww",
                           plottitle ="CV over time, NDRE, field 25 - Winter Wheat - 2022")

# Access results with new names
print(results_ndre_data25_cv_ww$anova_result_ndre_data25_cv_ww)

# Display plots with new names
print(results_ndre_data25_cv_ww$plot_residuals_no_int_ndre_data25_cv_ww)
print(results_ndre_data25_cv_ww$plot_residuals_int_ndre_data25_cv_ww)
print(results_ndre_data25_cv_ww$plot_response_ndre_data25_cv_ww)
print(results_ndre_data25_cv_ww$plot_qq_no_int_ndre_data25_cv_ww)
print(results_ndre_data25_cv_ww$plot_qq_int_ndre_data25_cv_ww)
```

#### CV NDVI sat Large-plot trial

```{r}
ndvi_data25$cv <- (ndvi_data25$std / ndvi_data25$mean)

# Run analysis for spring barley (2021)
results_ndvi_data25_cv_sb <- lme_analysis_lp(ndvi_data25, 
                           response_var = "cv", 
                           treatment_var = "Treatment",
                           plot_id_var = "PLOT_ID",
                           date_var = "timestamp",
                           start_date = start_date_sb, 
                           end_date = end_date_sb,
                           identifier = "sb",
                           plottitle = "CV over time, NDVI, field 25 - Spring Barley - 2021")

# Access results with new names
print(results_ndvi_data25_cv_sb$anova_result_ndvi_data25_cv_sb)

# Display plots with new names
print(results_ndvi_data25_cv_sb$plot_residuals_no_int_ndvi_data25_cv_sb)
print(results_ndvi_data25_cv_sb$plot_residuals_int_ndvi_data25_cv_sb)
print(results_ndvi_data25_cv_sb$plot_response_ndvi_data25_cv_sb)
print(results_ndvi_data25_cv_sb$plot_qq_no_int_ndvi_data25_cv_sb)
print(results_ndvi_data25_cv_sb$plot_qq_int_ndvi_data25_cv_sb)


# Run analysis for spring Winter wheat (2022)
results_ndvi_data25_cv_ww <- lme_analysis_lp(ndvi_data25, 
                           response_var = "cv", 
                           treatment_var = "Treatment",
                           plot_id_var = "PLOT_ID",
                           date_var = "timestamp",
                           start_date = start_date_ww, 
                           end_date = end_date_ww,
                           identifier = "ww",
                           plottitle ="CV over time, NDVI, field 25 - Winter Wheat - 2022")

# Access results with new names
print(results_ndvi_data25_cv_ww$anova_result_ndvi_data25_cv_ww)

# Display plots with new names
print(results_ndvi_data25_cv_ww$plot_residuals_no_int_ndvi_data25_cv_ww)
print(results_ndvi_data25_cv_ww$plot_residuals_int_ndvi_data25_cv_ww)
print(results_ndvi_data25_cv_ww$plot_response_ndvi_data25_cv_ww)
print(results_ndvi_data25_cv_ww$plot_qq_no_int_ndvi_data25_cv_ww)
print(results_ndvi_data25_cv_ww$plot_qq_int_ndvi_data25_cv_ww)
```

#### CV NDRE UAV Large-plot trial

```{r}

# Run analysis
results_ndre_data25_uav_cv_ww <- lme_analysis_lp_uav(ndre_data25_uav, 
                           response_var = "cv", 
                           treatment_var = "Treatment",
                           plot_id_var = "PLOT_ID",
                           date_var = "date",
                           start_date = start_date_ww, 
                           end_date = end_date_ww,
                           identifier = "ww",
                           plottitle = "CV for NDRE over time, large plot trial, Winter Wheat, 2022")



# Residuals plot without interaction
print(results_ndre_data25_uav_cv_ww$plot_residuals_no_int_ndre_data25_uav_cv_ww)

# Residuals plot with interaction
print(results_ndre_data25_uav_cv_ww$plot_residuals_int_ndre_data25_uav_cv_ww)
# Response plot
print(results_ndre_data25_uav_cv_ww$plot_response_ndre_data25_uav_cv_ww)
print(results_ndre_data25_uav_cv_ww$plot_qq_no_int_ndre_data25_uav_cv_ww)
print(results_ndre_data25_uav_cv_ww$plot_qq_int_ndre_data25_uav_cv_ww)

# ANOVA results
print(results_ndre_data25_uav_cv_ww$anova_result_ndre_data25_uav_cv_ww)
```

#### CV NDVI UAV Large-plot trial

```{r}
# Run analysis
results_ndvi_data25_uav_cv_ww <- lme_analysis_lp_uav(ndvi_data25_uav, 
                           response_var = "cv", 
                           treatment_var = "Treatment",
                           plot_id_var = "PLOT_ID",
                           date_var = "date",
                           start_date = start_date_ww, 
                           end_date = end_date_ww,
                           identifier = "ww",
                           plottitle = "CV for NDVI over time, large plot trial, Winter Wheat, 2022")



# Residuals plot without interaction
print(results_ndvi_data25_uav_cv_ww$plot_residuals_no_int_ndvi_data25_uav_cv_ww)
print(results_ndvi_data25_uav_cv_ww$plot_residuals_int_ndvi_data25_uav_cv_ww)
print(results_ndvi_data25_uav_cv_ww$plot_response_ndvi_data25_uav_cv_ww)
print(results_ndvi_data25_uav_cv_ww$plot_qq_no_int_ndvi_data25_uav_cv_ww)
print(results_ndvi_data25_uav_cv_ww$plot_qq_int_ndvi_data25_uav_cv_ww)
print(results_ndvi_data25_uav_cv_ww$anova_result_ndvi_data25_uav_cv_ww)

```

## Soil parameters

### UAV NDRE/NDVILargeplot

```{r}
# Function to create and analyze models with and without interaction terms
create_and_analyze_models <- function(data, response_var, parameter, year) {
  # Create formula strings for both model types
  interaction_formula <- as.formula(paste(response_var, "~", "T_", year, "*", parameter, "+ (1|PLOT_ID)", sep=""))
  no_interaction_formula <- as.formula(paste(response_var, "~", "T_", year, "+", parameter, "+ (1|PLOT_ID)", sep=""))
  
  # Fit both models
  model_int <- lmer(interaction_formula, data = data)
  model_no_int <- lmer(no_interaction_formula, data = data)
  
  # Compare models using ANOVA
  comparison <- anova(model_int, model_no_int)
  
  # Return all model results
  list(
    interaction = model_int,
    no_interaction = model_no_int,
    comparison = comparison
  )
}

# Function to create main effect plots showing relationship between variables
create_main_effect_plot <- function(data, y_var, x_var, treatment_year) {
  y_label <- if(grepl("NDVI", y_var)) "NDVI" else "NDRE"
  
  ggplot(data, aes_string(x = x_var, y = y_var, color = paste0("T_", treatment_year))) +
    geom_point(alpha = 0.5) +
    geom_smooth(method = "lm", formula = y ~ x, se = TRUE) +
    scale_color_manual(values = treatment_colors) +
    my_theme +
    labs(
      x = paste(x_var, "content"),
      y = y_label,
      color = "Treatment",
      title = paste(y_label, "vs", x_var, "by Treatment")
    )
}

# Function to create residual plots for model diagnostics
create_residual_plot <- function(model_data, treatment_year, response_var, parameter, interaction = TRUE) {
  y_label <- if(grepl("NDVI", response_var)) "NDVI" else "NDRE"
  interaction_text <- if(interaction) "With Interaction" else "Without Interaction"
  
  ggplot(model_data, aes(x = fitted, y = resid, color = Treatment)) +
    geom_point(alpha = 0.5) +
    geom_smooth(method = "loess", formula = y ~ x, se = TRUE) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
    scale_color_manual(values = treatment_colors) +
    theme_minimal() +
    labs(
      x = "Fitted values",
      y = "Residuals",
      title = paste(y_label, "vs", parameter, "-", interaction_text)
    )
}

create_qq_plot <- function(model_data, treatment_year, response_var, parameter, interaction = TRUE) {
  y_label <- if(grepl("NDVI", response_var)) "NDVI" else "NDRE"
  interaction_text <- if(interaction) "With Interaction" else "Without Interaction"
  
  ggplot(data.frame(resid = residuals(model_data)), aes(sample = resid)) +
    stat_qq() +
    stat_qq_line() +
    theme_minimal() +
    labs(
      x = "Theoretical Quantiles",
      y = "Sample Quantiles",
      title = paste(y_label, "vs", parameter, "QQ Plot -", interaction_text)
    )
}


# Define analysis arameters - this is what i change! Call str() and see possibilities
parameters <- c("humus", "ph", "clay")
response_vars <- c("NDVI_b1_mean", "NDRE0517_b1_mean")

# Initialize results storage
all_results <- data.frame()

# Generate all models and store results
for(response_var in response_vars) {
  for(param in parameters) {
    models <- create_and_analyze_models(voronoi_withinlargeplots_25, response_var, param, "2022")
    
    result <- data.frame(
      Index = ifelse(grepl("NDVI", response_var), "NDVI", "NDRE"),
      Year = "2022",
      Parameter = param,
      L.Ratio = models$comparison$Chisq[2],
      Num_DF = models$comparison$Df[2],
      Den_DF = df.residual(models$interaction),
      p.value = models$comparison$`Pr(>Chisq)`[2]
    )
    
    all_results <- rbind(all_results, result)
  }
}

# plot storage
ndvi_main_plots <- list()
ndre_main_plots <- list()
ndvi_residual_plots <- list()
ndre_residual_plots <- list()
ndvi_qq_plots <- list()
ndre_qq_plots <- list()


#  plots for each parameter
for(param in parameters) {
  # Main effect plots
  ndvi_main_plots[[param]] <- create_main_effect_plot(voronoi_withinlargeplots_25, 
                                                     "NDVI_b1_mean", param, "2022")
  ndre_main_plots[[param]] <- create_main_effect_plot(voronoi_withinlargeplots_25, 
                                                     "NDRE0517_b1_mean", param, "2022")
  
  # Models and residual plots for NDVI
  ndvi_models <- create_and_analyze_models(voronoi_withinlargeplots_25, 
                                         "NDVI_b1_mean", param, "2022")
  
  # Create residual plots for NDVI
  ndvi_residual_no_int <- create_residual_plot(
    data.frame(
      fitted = fitted(ndvi_models$no_interaction),
      resid = residuals(ndvi_models$no_interaction),
      Treatment = voronoi_withinlargeplots_25$T_2022,
      Model = "no_interaction"
    ), "2022", "NDVI", param, interaction = FALSE
  )
  
  ndvi_residual_int <- create_residual_plot(
    data.frame(
      fitted = fitted(ndvi_models$interaction),
      resid = residuals(ndvi_models$interaction),
      Treatment = voronoi_withinlargeplots_25$T_2022,
      Model = "interaction"
    ), "2022", "NDVI", param, interaction = TRUE
  )
  ndvi_qq_no_int <- create_qq_plot(ndvi_models$no_interaction, 
                                  "2022", "NDVI", param, 
                                  interaction = FALSE)
  
  ndvi_qq_int <- create_qq_plot(ndvi_models$interaction, 
                               "2022", "NDVI", param, 
                               interaction = TRUE)
  
  
  # name NDVI inspection plots
  ndvi_residual_plots[[paste0(param, "_1")]] <- ndvi_residual_no_int
  ndvi_residual_plots[[paste0(param, "_2")]] <- ndvi_residual_int
  ndvi_qq_plots[[paste0(param, "_no_int")]] <- ndvi_qq_no_int
  ndvi_qq_plots[[paste0(param, "_int")]] <- ndvi_qq_int
  
  # Models and residual plots for NDRE
  ndre_models <- create_and_analyze_models(voronoi_withinlargeplots_25, 
                                         "NDRE0517_b1_mean", param, "2022")
  
  # residual plots for NDRE
  ndre_residual_no_int <- create_residual_plot(
    data.frame(
      fitted = fitted(ndre_models$no_interaction),
      resid = residuals(ndre_models$no_interaction),
      Treatment = voronoi_withinlargeplots_25$T_2022,
      Model = "no_interaction"
    ), "2022", "NDRE", param, interaction = FALSE
  )
  
  ndre_residual_int <- create_residual_plot(
    data.frame(
      fitted = fitted(ndre_models$interaction),
      resid = residuals(ndre_models$interaction),
      Treatment = voronoi_withinlargeplots_25$T_2022,
      Model = "interaction"
    ), "2022", "NDRE", param, interaction = TRUE
  )
  ndre_qq_no_int <- create_qq_plot(ndre_models$no_interaction, 
                                  "2022", "NDRE", param, 
                                  interaction = FALSE)
  
  ndre_qq_int <- create_qq_plot(ndre_models$interaction, 
                               "2022", "NDRE", param, 
                               interaction = TRUE)
  
  # name NDRE residual plots
  ndre_residual_plots[[paste0(param, "_1")]] <- ndre_residual_no_int
  ndre_residual_plots[[paste0(param, "_2")]] <- ndre_residual_int
   ndre_qq_plots[[paste0(param, "_no_int")]] <- ndre_qq_no_int
  ndre_qq_plots[[paste0(param, "_int")]] <- ndre_qq_int
}
ndre_main_plots$ph <- ndre_main_plots$ph + xlab("pH")
ndvi_main_plots$ph <- ndvi_main_plots$ph + xlab("pH")

#Print
print(ndre_residual_plots)
print(ndvi_residual_plots)
print(ndre_main_plots)
print(ndvi_main_plots)
print(ndre_models)
print(ndvi_models)
print(all_results)
print(ndvi_qq_plots)
print(ndre_qq_plots)
```

### UAV NDRE/NDVI Small plot

```{r}
# create model and plots for each soil parameter
analyze_soil_parameter <- function(data, parameter, response_var, treatment_colors, index_name) {
  # Fit models 
  model_interaction <- lmer(paste0(response_var, " ~ Treatment_2022 * ", parameter, 
                                 " + (1|PLOT_ID) + (1|Block_a)"), 
                          weights = area,
                          data = data)
  model_no_interaction <- lmer(paste0(response_var, " ~ Treatment_2022 + ", parameter, 
                                    " + (1|PLOT_ID) + (1|Block_a)"), 
                             weights = area,
                             data = data)
  
  # Create QQ plots
  qq_int <- ggplot(data.frame(resid = residuals(model_interaction)), 
                   aes(sample = resid)) +
    stat_qq() +
    stat_qq_line() +
    my_theme +
    labs(title = paste0(index_name, " QQ Plot - ", str_to_title(parameter), " with interaction"),
         x = "Theoretical Quantiles",
         y = "Sample Quantiles")

  qq_no_int <- ggplot(data.frame(resid = residuals(model_no_interaction)), 
                      aes(sample = resid)) +
    stat_qq() +
    stat_qq_line() +
    my_theme +
    labs(title = paste0(index_name, " QQ Plot - ", str_to_title(parameter), " without interaction"),
         x = "Theoretical Quantiles",
         y = "Sample Quantiles")
  
  # Customize x-axis label based on parameter
  x_label <- case_when(
    parameter == "ph" ~ "pH",
    TRUE ~ paste0(str_to_title(parameter), " Content (%)")
  )
  
  # Create scatter plot
  p <- ggplot(data, aes_string(x = parameter, y = response_var, color = "Treatment_2022")) +
    geom_point(alpha = 0.5) +
    geom_smooth(method = "lm", formula = y ~ x, se = FALSE) +
    scale_color_manual(values = treatment_colors, name = "Treatment") +
    my_theme +
    labs(
      x = x_label,
      y = index_name,
      title = paste0(index_name, "-response to ", str_to_title(parameter), 
                    ifelse(parameter == "ph", "", " content"), " by Treatment")
    )
    
  # Return both models and plots
  list(
    interaction = model_interaction,
    no_interaction = model_no_interaction,
    plot = p,
    qq_int = qq_int,
    qq_no_int = qq_no_int,
    anova = anova(model_interaction, model_no_interaction)
  )
}

# Define parameters to analyze 
soil_params <- c("clay", "ph")

# Analyze NDRE
ndre_results <- lapply(soil_params, function(param) {
  analyze_soil_parameter(voronoi_within_smallplot_full_26_nonresdata, 
                        param, "NDRE0517_uav", treatment_colors, "NDRE")
})
names(ndre_results) <- soil_params

# Analyze NDVI
ndvi_results <- lapply(soil_params, function(param) {
  analyze_soil_parameter(voronoi_within_smallplot_full_26_nonresdata, 
                        param, "NDVI0517_uav", treatment_colors, "NDVI")
})
names(ndvi_results) <- soil_params

# Combine plots for NDRE
ndre_plots <- lapply(ndre_results, function(x) x$plot)
ndre_plots$ph <- ndre_plots$ph + labs(title="NDRE-response to pH by treatment")
ndre_combined <- ggarrange(plotlist = ndre_plots, 
                          ncol = 2, 
                          nrow = 1,
                          common.legend = TRUE,
                          legend = "bottom",
                          legend.grob = get_legend(ndre_plots[[1]] + 
                                                 theme(legend.position = "bottom",
                                                      legend.direction = "horizontal")))

# Combine plots for NDVI
ndvi_plots <- lapply(ndvi_results, function(x) x$plot)
ndvi_plots$ph <- ndvi_plots$ph + labs(title="NDVI-response to pH by treatment")

# Print results
list(ndvi_plots)
list(ndre_plots)
print(all_results)

# Print QQ plots for NDVI
for(param in soil_params) {
  print(ndvi_results[[param]]$qq_no_int)
  print(ndvi_results[[param]]$qq_int)
}

# Print QQ plots for NDRE
for(param in soil_params) {
  print(ndre_results[[param]]$qq_no_int)
  print(ndre_results[[param]]$qq_int)
}

```

### Satellite NDRE/NDVI

```{r}
# Prepare datasets for both years
data_2021 <- reflectance_soiloptix_largeplot25_satelite %>%
  filter(timestamp >= start_date_sb,
         timestamp <= end_date_sb) %>%
  mutate(Treatment = Treatment_2021,
         timeSinceStart = as.numeric(timestamp - start_date_sb))

data_2022 <- reflectance_soiloptix_largeplot25_satelite %>%
  filter(timestamp >= start_date_ww,
         timestamp <= end_date_ww) %>%
  mutate(Treatment = Treatment_2022,
         timeSinceStart = as.numeric(timestamp - start_date_ww))

# Function to fit models for both indices
fit_models <- function(data, index, param) {
  # Formula for models
  formula_int <- as.formula(paste(index, "~ Treatment * timeSinceStart *", param, ""))
  formula_no_int <- as.formula(paste(index, "~ Treatment * timeSinceStart + ", param, ""))
  
  # Fit models
  model_int <- lme(formula_int,
                  random = ~1|PLOT_ID,
                  correlation = corAR1(form = ~timeSinceStart|PLOT_ID),
                  data = data)
  
  model_no_int <- lme(formula_no_int,
                     random = ~1|PLOT_ID,
                     correlation = corAR1(form = ~timeSinceStart|PLOT_ID),
                     data = data)
  
  # Compare models
  comparison <- anova(model_int, model_no_int)
  
  return(list(
    int = model_int,
    no_int = model_no_int,
    comparison = comparison
  ))
}

# Fit models for all parameters and both indices
params <- c("clay", "humus", "ph")
indices <- c("NDVI", "NDRE")
years <- list("2021" = data_2021, "2022" = data_2022)

# Store all model results
all_models <- list()
for(year_name in names(years)) {
  all_models[[year_name]] <- list()
  for(index in indices) {
    all_models[[year_name]][[index]] <- list()
    for(param in params) {
      all_models[[year_name]][[index]][[param]] <- 
        fit_models(years[[year_name]], index, param)
    }
  }
}

# Function to create plots with updated styling
create_index_plot <- function(data, index, year) {
  p <- ggplot(data, aes(x = timeSinceStart, y = get(index), color = Treatment)) +
    geom_point(alpha = 0.5) +
    geom_smooth() +
    facet_wrap(~cut(clay, breaks = 3),
              labeller = labeller(
                clay = function(x) paste("Clay Content:", x, "%")
              )) +
    my_theme +  # Apply your custom theme
    labs(title = paste(year, index, "over time by Treatment and Clay Content"),
         x = paste("Days since", ifelse(year == "2021", "April 1st, 2021", "March 30th, 2022")),
         y = index)
  
  # Only add horizontal bottom legend for 2022
  if(year == "2022") {
    p <- p + theme(
      legend.position = "bottom",
      legend.direction = "horizontal",
      legend.box = "horizontal",
      legend.margin = margin(t = 20)  # Add some space above the legend
    )
  } else {
    p <- p + theme(legend.position = "none")  # Remove legend for 2021
  }
  
  return(p)
}

# Extract results for table
extract_model_results <- function(models) {
  results <- data.frame(
    Index = character(),
    Year = character(),
    Parameter = character(),
    L_Ratio = numeric(),
    p_value = character(),
    stringsAsFactors = FALSE
  )
  
  for(year_name in names(models)) {
    for(index in names(models[[year_name]])) {
      for(param in names(models[[year_name]][[index]])) {
        comparison <- models[[year_name]][[index]][[param]]$comparison
        
        results <- rbind(results, data.frame(
          Index = index,
          Year = year_name,
          Parameter = case_when(
            param == "ph" ~ "pH",
            param == "fineSand" ~ "Fine Sand",
            TRUE ~ str_to_title(param)
          ),
          L_Ratio = comparison$L.Ratio[2],
          p_value = ifelse(comparison$`p-value`[2] < 0.001,
                          "< 0.001",
                          sprintf("%.3f", comparison$`p-value`[2]))
        ))
      }
    }
  }
  
  return(results)
}

# Create and format table
model_results <- extract_model_results(all_models) %>%
  mutate(
    H_0 = "Reflectance ~ Treatment  Time + Parameter",
    H_1 = "Reflectance ~ Treatment  time  Parameter"
  )


print(model_results)

# comparison results for each case
for(year_name in names(all_models)) {
  for(index in indices) {
    for(param in params) {
      print(all_models[[year_name]][[index]][[param]]$comparison)
    }
  }
}

# Create and print QQ plots for model diagnostics
for(year_name in names(all_models)) {
  for(index in indices) {
    for(param in params) {
      # QQ plot for model with interaction
      qq_int <- ggplot(data.frame(resid = residuals(all_models[[year_name]][[index]][[param]]$int)), 
                      aes(sample = resid)) +
        stat_qq() +
        stat_qq_line() +
        labs(title = paste(index, year_name, param, "- Model with interaction"),
             x = "Theoretical Quantiles",
             y = "Sample Quantiles")
      print(qq_int)
      
      # QQ plot for model without interaction
      qq_no_int <- ggplot(data.frame(resid = residuals(all_models[[year_name]][[index]][[param]]$no_int)), 
                         aes(sample = resid)) +
        stat_qq() +
        stat_qq_line() +
        labs(title = paste(index, year_name, param, "- Model without interaction"),
             x = "Theoretical Quantiles",
             y = "Sample Quantiles")
      print(qq_no_int)
    }
  }
}

# Print summary of a few example models
print(summary(all_models[["2022"]][["NDVI"]][["clay"]]$int))
print(summary(all_models[["2022"]][["NDRE"]][["clay"]]$int))
print(summary(all_models[["2022"]][["NDVI"]][["ph"]]$int))
print(summary(all_models[["2022"]][["NDRE"]][["ph"]]$int))
print(summary(all_models[["2022"]][["NDVI"]][["humus"]]$int))
print(summary(all_models[["2022"]][["NDRE"]][["humus"]]$int))

# Create and print main plots
for(year_name in names(years)) {
  for(index in indices) {
    for(param in params) {
    main_plot <- create_index_plot(years[[year_name]], index, year_name)
    print(main_plot)
  }
}}

# Create and print residual plots
for(year_name in names(all_models)) {
  for(index in indices) {
    for(param in params) {
      # Residual plot for model with interaction
      res_int <- ggplot(data.frame(
        fitted = fitted(all_models[[year_name]][[index]][[param]]$int),
        resid = residuals(all_models[[year_name]][[index]][[param]]$int),
        Treatment = years[[year_name]]$Treatment), 
        aes(x = fitted, y = resid, color = Treatment)) +
        geom_point(alpha = 0.5) +
        geom_smooth(method = "loess", se = FALSE) +
        geom_hline(yintercept = 0, linetype = "dashed") +
        scale_color_manual(values = treatment_colors) +
        my_theme +
        labs(title = paste(index, year_name, param, "- Residuals (with interaction)"),
             x = "Fitted values",
             y = "Residuals")
      print(res_int)
      
      # Residual plot for model without interaction
      res_no_int <- ggplot(data.frame(
        fitted = fitted(all_models[[year_name]][[index]][[param]]$no_int),
        resid = residuals(all_models[[year_name]][[index]][[param]]$no_int),
        Treatment = years[[year_name]]$Treatment), 
        aes(x = fitted, y = resid, color = Treatment)) +
        geom_point(alpha = 0.5) +
        geom_smooth(method = "loess", se = FALSE) +
        geom_hline(yintercept = 0, linetype = "dashed") +
        scale_color_manual(values = treatment_colors) +
        my_theme +
        labs(title = paste(index, year_name, param, "- Residuals (without interaction)"),
             x = "Fitted values",
             y = "Residuals")
      print(res_no_int)
    }
  }
}
```

## Method validation

### Correlating drone and satellite data 

```{r}
# Helper function to format dates consistently
format_date <- function(d) {
  if(is.numeric(d)) {
    return(ymd(as.character(d)))
  } else if(is.Date(d)) {
    return(d)
  }
}

# Field 25 NDVI
field25_sat_ndvi <- reflectance_soiloptix_largeplot25_satelite %>%
  dplyr::select(PLOT_ID, timestamp, NDVI) %>%
  mutate(sat_date = format_date(timestamp)) %>%
  rename(satellite_ndvi = NDVI)

field25_uav_ndvi <- ndvi_uav_field25 %>%
  mutate(uav_date = format_date(date))


# Join 
field25_ndvi_comparison <- field25_uav_ndvi %>%
  inner_join(field25_sat_ndvi, by = "PLOT_ID") %>%
  group_by(PLOT_ID, uav_date) %>%
  slice_min(order_by = abs(as.numeric(sat_date - uav_date)), n = 1) %>%
  ungroup()

# plotting function with statistics
plot_with_stats <- function(data, x_var, y_var, title) {
  # linear model
  lm_fit <- lm(as.formula(paste(y_var, "~", x_var)), data = data)
  
  #  statistics
  slope <- round(coef(lm_fit)[2], 3)
  r_squared <- round(summary(lm_fit)$r.squared, 3)
  p_value <- round(summary(lm_fit)$coefficients[2,4], 3)
  
  #  annotation text
  stats_text <- sprintf("Slope = %s\nR = %s\np-value = %s", 
                       slope, r_squared, 
                       ifelse(p_value < 0.001, "< 0.001", p_value))
  
  ggplot(data, aes(x = .data[[x_var]], y = .data[[y_var]])) +
    geom_point(aes(color = as.factor(uav_date))) +
    geom_smooth(method = "lm", se = FALSE) +
    annotate("text", x = min(data[[x_var]]), 
             y = max(data[[y_var]]), 
             label = stats_text,
             hjust = 0, vjust = 1,
             size = 8) +
    labs(title = title,
         x = stringr::str_replace(x_var, "mean", "UAV"),
         y = stringr::str_replace(y_var, "satellite_", "Satellite "),
         color = "UAV Date") +
    theme_minimal()+
    theme(legend.text = element_text(size = 18))
}

#  first plot
p1 <- plot_with_stats(field25_ndvi_comparison, "mean", "satellite_ndvi", 
                      "Large-plot trial - NDVI Correlation")

# Field 25 NDRE
field25_sat_ndre <- reflectance_soiloptix_largeplot25_satelite %>%
  dplyr::select(PLOT_ID, timestamp, NDRE) %>%
  mutate(sat_date = format_date(timestamp)) %>%
  rename(satellite_ndre = NDRE)

field25_uav_ndre <- ndre_uav_field25 %>%
  mutate(uav_date = format_date(date))

field25_ndre_comparison <- field25_uav_ndre %>%
  inner_join(field25_sat_ndre, by = "PLOT_ID") %>%
  group_by(PLOT_ID, uav_date) %>%
  slice_min(order_by = abs(as.numeric(sat_date - uav_date)), n = 1) %>%
  ungroup()

# Create remaining plots
p2 <- plot_with_stats(field25_ndre_comparison, "mean", "satellite_ndre", 
                      "Large-plot trial - NDRE Correlation")

# Field 26 NDVI
field26_sat_ndvi <- reflectance_soiloptix_26_satelite %>%
  dplyr::select(PLOT_ID, timestamp, NDVI_mean) %>%
  mutate(sat_date = format_date(timestamp)) %>%
  rename(satellite_ndvi = NDVI_mean)

field26_uav_ndvi <- bind_rows(
  ndvi_uav_field26,
  ndvi_uav_field26_residual
) %>%
  mutate(uav_date = format_date(date))

field26_ndvi_comparison <- field26_uav_ndvi %>%
  inner_join(field26_sat_ndvi, by = "PLOT_ID") %>%
  group_by(PLOT_ID, uav_date) %>%
  slice_min(order_by = abs(as.numeric(sat_date - uav_date)), n = 1) %>%
  ungroup()

p3 <- plot_with_stats(field26_ndvi_comparison, "mean", "satellite_ndvi", 
                      "Small-plot trial - NDVI Correlation")

# Field 26 NDRE
field26_sat_ndre <- reflectance_soiloptix_26_satelite %>%
  dplyr::select(PLOT_ID, timestamp, NDRE_mean) %>%
  mutate(sat_date = format_date(timestamp)) %>%
  rename(satellite_ndre = NDRE_mean)

field26_uav_ndre <- bind_rows(
  ndre_uav_field26,
  ndre_uav_field26_residual
) %>%
  mutate(uav_date = format_date(date))

field26_ndre_comparison <- field26_uav_ndre %>%
  inner_join(field26_sat_ndre, by = "PLOT_ID") %>%
  group_by(PLOT_ID, uav_date) %>%
  slice_min(order_by = abs(as.numeric(sat_date - uav_date)), n = 1) %>%
  ungroup()

p4 <- plot_with_stats(field26_ndre_comparison, "mean", "satellite_ndre", 
                      "Small-plot trial - NDRE Correlation")

# Remove individual legends
p1 <- p1 + my_theme 
p2 <- p2 + my_theme 
p3 <- p3 + my_theme
p4 <- p4 + my_theme 

print(p1)
print(p2)
print(p3)
print(p4)
```

Correlating with harvest data UAV

```{r}
ndre_data25 <- read_csv(here("data", "ndre_data25.csv"))
ndvi_data25 <- read_csv(here("data", "ndvi_data25.csv"))
ndre_data25_uav <- read_csv(here("data", "ndre_uav_field25.csv"))
ndvi_data25_uav <- read_csv(here("data", "ndvi_uav_field25.csv"))
ndvi_data26 <- read_csv(here("data", "ndvi_data26.csv")) 
ndvi_data26_residual <- read_csv(here("data", "ndvi_data26_residual.csv"))
ndre_data26 <- read_csv(here("data", "ndre_data26.csv")) 
ndre_data26_residual <- read_csv(here("data", "ndre_data26_residual.csv"))
ndre_data26 <- read_csv(here("data", "ndre_data26.csv")) 
ndvi_uav_field26 <- read_csv(here("data", "ndvi_uav_field26.csv"))
ndvi_uav_field26_residual <- read_csv(here("data", "ndvi_uav_field26_residual.csv"))
voronoi_withinlargeplots_25 <- read_csv(here("data","voronoi_withinlargeplots_25_2_UAV.csv"))
voronoi_within_smallplot_full_26_nonresdata <- read_csv(here("data","voronoi_within_smallplot_full_26_nonresdata.csv"))
reflectance_soiloptix_largeplot25_satelite <- read_csv(here("data","reflectance_soiloptix_largeplot25_satelite.csv"))

ndvi_uav_field25 <- read_csv(here("data", "ndvi_uav_field25.csv"))
ndre_uav_field25 <- read_csv(here("data", "ndre_uav_field25.csv"))
ndvi_uav_field26 <- read_csv(here("data", "ndvi_uav_field26.csv"))
ndre_uav_field26 <- read_csv(here("data", "ndre_uav_field26.csv"))
ndre_uav_field26_residual <- read_csv(here("data", "ndre_uav_field26_residual.csv"))
ndvi_uav_field26_residual <- read_csv(here("data", "ndvi_uav_field26_residual.csv"))
reflectance_soiloptix_26_satelite <- read_csv(here("data", "reflectance_soiloptix_26.csv"))
reflectance_soiloptix_26_res_sat <- read_csv(here("data", "reflectance_soiloptix_26_res_sat.csv"))
harvest_field25 <- read_csv(here("data", "harvest_field25.csv"))
harvest_field26 <- read_csv(here("data", "harvest_field26.csv"))
ndre_data25_2 <- read_csv(here("data", "ndre_data25_2.csv"))
ndvi_data25_2 <- read_csv(here("data", "ndvi_data25_2.csv"))
```

```{r}
 #Functi 25 data
process_field25 <- function(ndvi_data, ndre_data, harvest_data) {
  ndvi_data <- ndvi_data %>%
    mutate(date = as.Date(as.character(date), format = "%Y%m%d")) %>%
    dplyr::select(PLOT_ID, date, NDVI_mean = mean)
  
  ndre_data <- ndre_data %>%
    mutate(date = as.Date(as.character(date), format = "%Y%m%d")) %>%
    dplyr::select(PLOT_ID, date, NDRE_mean = mean)
  
  field25 <- ndvi_data %>%
    left_join(ndre_data, by = c("PLOT_ID", "date")) %>%
    left_join(
      harvest_data %>%
        dplyr::select(
          PLOT_ID,
          harvest_2021 = `Harvest 06-08-2021 harvestable (grain) yield 15 % moisture (kg/ha)`,
          harvest_2022 = `Harvest 11-08-2022 harvestable (grain) yield 15 % moisture (kg/ha)`
        ),
      by = "PLOT_ID"
    )
  
  return(field25)
}

# Function 26 data
process_field26 <- function(ndvi_data, ndre_data, harvest_data) {
  ndvi_data <- ndvi_data %>%
    mutate(date = as.Date(as.character(date), format = "%Y%m%d")) %>%
    dplyr::select(PLOT_ID, date, NDVI_mean = mean)
  
  ndre_data <- ndre_data %>%
    mutate(date = as.Date(as.character(date), format = "%Y%m%d")) %>%
    dplyr::select(PLOT_ID, date, NDRE_mean = mean)
  
  field26 <- ndvi_data %>%
    left_join(ndre_data, by = c("PLOT_ID", "date")) %>%
    left_join(
      harvest_data %>%
        dplyr::select(
          PLOT_ID,
          harvest_2021 = `Harvest 06-08-2021 harvestable (grain) yield 15 % moisture (kg/ha)`,
          harvest_2022 = `Harvest 11-08-2022 harvestable (grain) yield 15 % moisture (kg/ha)`,
          biomass_2021 = `16-11-2021 Biomass dryweight (kg/ha)`,
          biomass_2022 = `Anthesis 31-05-2022 Biomass dryweight (kg/ha)`
        ),
      by = "PLOT_ID"
    )
  
  return(field26)
}

create_relationship_plot <- function(data, y_col, x_col, x_label, y_label, trial_name) {
  y_sym <- sym(y_col)
  x_sym <- sym(x_col)
  
  plot_data <- data %>%
    filter(date == as.Date("2022-05-17")) %>%
    drop_na(!!y_sym, !!x_sym)
  
  model_formula <- as.formula(paste(y_col, "~", x_col))
  model <- lm(model_formula, data = plot_data)
  model_summary <- summary(model)
  
  r_squared <- model_summary$r.squared
  p_value <- anova(model)$`Pr(>F)`[1]
  
  # Format p-value
  p_value_text <- if(p_value < 0.001) {
    "p < 0.001"
  } else if(p_value < 0.01) {
    "p < 0.01"
  } else if(p_value < 0.05) {
    "p < 0.05"
  } else {
    sprintf("p = %.3f", p_value)
  }
  
  correlation <- cor(plot_data[[y_col]], plot_data[[x_col]])
  slope <- coef(model)[2]
  
  p <- ggplot(plot_data, aes(x = !!x_sym, y = !!y_sym)) +
    geom_point(alpha = 0.6) +
    geom_smooth(method = "lm", color = "blue") +
    labs(
      x = paste("UAV", x_label),
      y = y_label,
      title = paste(trial_name, "-", y_label, "vs", "UAV", x_label),
      subtitle = sprintf(
        "Slope: %.2f, Correlation: %.3f, %s",
        slope, r_squared, p_value_text  # Changed to use p_value_text
      )
    ) +
    theme_minimal() +
    theme(
      plot.title = element_text(size = 12),
      plot.subtitle = element_text(size =12)
    )
  
  return(list(plot = p, stats = list(
    slope = slope,
    r_squared = r_squared,
    correlation = correlation,
    p_value = p_value
  )))
}

# Process data
field25 <- process_field25(ndvi_uav_field25, ndre_uav_field25, harvest_field25)
field26 <- process_field26(ndvi_uav_field26, ndre_uav_field26, harvest_field26)

# plots for Large-plot trial
field25_plots <- list(
  ndvi_yield = create_relationship_plot(
    field25, "harvest_2022", "NDVI_mean",
    "NDVI (May 17, 2022)", "Harvest Yield 2022 (kg/ha)",
    "Large-plot trial"
  ),
  ndre_yield = create_relationship_plot(
    field25, "harvest_2022", "NDRE_mean",
    "NDRE (May 17, 2022)", "Harvest Yield 2022 (kg/ha)",
    "Large-plot trial"
  )
)

# Create plots for Small-plot trial (Field 26)
field26_plots <- list(
  ndvi_yield = create_relationship_plot(
    field26, "harvest_2022", "NDVI_mean",
    "NDVI (May 17, 2022)", "Harvest Yield 2022 (kg/ha)",
    "Small-plot trial"
  ),
  ndre_yield = create_relationship_plot(
    field26, "harvest_2022", "NDRE_mean",
    "NDRE (May 17, 2022)", "Harvest Yield 2022 (kg/ha)",
    "Small-plot trial"
  ),
  ndvi_biomass = create_relationship_plot(
    field26, "biomass_2022", "NDVI_mean",
    "NDVI (May 17, 2022)", "Biomass 2022 (kg/ha)",
    "Small-plot trial"
  ),
  ndre_biomass = create_relationship_plot(
    field26, "biomass_2022", "NDRE_mean",
    "NDRE (May 17, 2022)", "Biomass 2022 (kg/ha)",
    "Small-plot trial"
  )
)

# Print all plots
print(field25_plots$ndvi_yield$plot)
print(field25_plots$ndre_yield$plot)
print(field26_plots$ndvi_yield$plot)
print(field26_plots$ndre_yield$plot)
print(field26_plots$ndvi_biomass$plot)
print(field26_plots$ndre_biomass$plot)

# Create summary statistics table
stats_table <- data.frame(
  Trial = c(
    rep("Large-plot", 2),
    rep("Small-plot", 4)
  ),
  Relationship = c(
    "NDVI vs Yield",
    "NDRE vs Yield",
    "NDVI vs Yield",
    "NDRE vs Yield",
    "NDVI vs Biomass",
    "NDRE vs Biomass"
  ),
  R_squared = c(
    field25_plots$ndvi_yield$stats$r_squared,
    field25_plots$ndre_yield$stats$r_squared,
    field26_plots$ndvi_yield$stats$r_squared,
    field26_plots$ndre_yield$stats$r_squared,
    field26_plots$ndvi_biomass$stats$r_squared,
    field26_plots$ndre_biomass$stats$r_squared
  ),
  P_value = c(
    field25_plots$ndvi_yield$stats$p_value,
    field25_plots$ndre_yield$stats$p_value,
    field26_plots$ndvi_yield$stats$p_value,
    field26_plots$ndre_yield$stats$p_value,
    field26_plots$ndvi_biomass$stats$p_value,
    field26_plots$ndre_biomass$stats$p_value
  ),
  Slope = c(
    field25_plots$ndvi_yield$stats$slope,
    field25_plots$ndre_yield$stats$slope,
    field26_plots$ndvi_yield$stats$slope,
    field26_plots$ndre_yield$stats$slope,
    field26_plots$ndvi_biomass$stats$slope,
    field26_plots$ndre_biomass$stats$slope
  )
)

# Format table
stats_table <- stats_table %>%
  mutate(
    R_squared = round(R_squared, 3),
    P_value = case_when(
      P_value < 0.001 ~ "< 0.001",
      P_value < 0.01 ~ "< 0.01",
      P_value < 0.05 ~ "< 0.05",
      TRUE ~ sprintf("%.3f", P_value)
    ),
    Slope = round(Slope, 2)
  )

# Print formatted table
print(knitr::kable(stats_table, format = "markdown"))
```

### Correlating with harvest data Sat

#### Code used for the thesis 26

This code actually takes the individual max NDVI for individual treatments, and are wrong

```{r}
# Funcmaximum index ate
get_max_index <- function(data, target_date) {
  # Date 
  target_date <- as.Date(target_date)
  
  # Group by PLOT_ID and find maximum index before target date
  max_indices <- data %>%
    filter(as.Date(timestamp) <= target_date) %>%
    group_by(PLOT_ID) %>%
    summarize(
      max_index = max(mean, na.rm = TRUE),
      date_max = timestamp[which.max(mean)],
      Treatment = first(Treatment),
      Year_estab = first(Year_estab),
      .groups = 'drop'
    )
  
  return(max_indices)
}

# Function to create scatter plot
create_single_scatter_plot <- function(data, target_date, biomass_col, estab_year, index_type="NDVI") {
  # Filter establishment observation year
  obs_year <- as.numeric(format(as.Date(target_date), "%Y"))
  
  plot_data <- data %>%
    filter(Year_estab == estab_year,
           Year_obs == obs_year)
  
  #  maximum values beforedate
  max_index_data <- get_max_index(plot_data, target_date)
  
  # biomass values per plot
  biomass_data <- plot_data %>%
    dplyr::select(PLOT_ID, !!sym(biomass_col)) %>%
    distinct()
  
  # Combine index and biomass data
  plot_data <- max_index_data %>%
    inner_join(biomass_data, by = "PLOT_ID")
  
  # Remove NA values
  plot_data <- na.omit(plot_data)
  
  # Calculate statistics 
  if(nrow(plot_data) >= 3) {
    # Fit model and get statistics
    model <- lm(get(biomass_col) ~ max_index, data = plot_data)
    r_squared <- round(summary(model)$r.squared, 3)
    correlation <- round(cor(plot_data$max_index, plot_data[[biomass_col]]), 3)
    p_value <- summary(model)$coefficients[2,4]  # Removed rounding
    slope <- round(coef(model)[2], 0)
    
    # Format dates
    target_date_str <- format(as.Date(target_date), "%d %B %Y")
    max_index_date <- format(as.Date(names(which.max(table(plot_data$date_max)))), "%d %B %Y")
    
    #  harvest yield or biomass based on the target date
    target_month <- format(as.Date(target_date), "%m")
    measurement_type <- if(target_month == "08") "Harvest Yield" else "Biomass"
    
    # Format p-value with thresholds
    p_value_text <- if(p_value < 0.001) {
        "p < 0.001"
    } else if(p_value < 0.01) {
        "p < 0.01"
    } else if(p_value < 0.05) {
        "p < 0.05"
    } else {
        sprintf("p = %.3f", p_value)
    }
    
    p <- ggplot(plot_data, aes(x = max_index, y = .data[[biomass_col]], color = Treatment)) +
      geom_point(alpha = 0.6, size = 3) +
      geom_smooth(method = "lm", color = "black", se = TRUE, linewidth = 1) +
      theme_minimal() +
      scale_color_manual(values = treatment_colors) +
      labs(
        title = paste(index_type, "vs", measurement_type, "-", "Establishment Year:", estab_year),
        subtitle = paste0(
          "Max ", index_type, " from: ", max_index_date, "  |  ",
          measurement_type, " from: ", target_date_str, "\n",
          "R = ", r_squared, "  |  ",
          p_value_text, "  |  ",  # Changed to use p_value_text directly
          "Correlation = ", correlation
        ),
        x = paste("Maximum", index_type),
        y = paste(measurement_type, "(kg/ha)")
      ) +
      theme(
        plot.title = element_text(size = 11, face = "bold"),
        plot.subtitle = element_text(size = 9),
        axis.title = element_text(size = 10),
        legend.position = "bottom",
        plot.margin = margin(t = 10, r = 10, b = 10, l = 10)
      )
    
    return(p)
  }
}

# Define analysis pairs
analysis_pairs <- list(
  list(
    date = "2021-06-23",
    biomass = "Anthesis_23062021_Biomass_dryweight_kgha",
    estab_year = 2021
  ),
  list(
    date = "2021-08-06",
    biomass = "Harvest_06082021_harvestable_grain_yield_15_moisture_kgha",
    estab_year = 2021
  ),
  list(
    date = "2022-05-31",
    biomass = "Anthesis_31052022_Biomass_dryweight_kgha",
    estab_year = 2022
  ),
  list(
    date = "2022-08-11",
    biomass = "Harvest_11082022_harvestable_grain_yield_15_moisture_kgha",
    estab_year = 2022
  )
)

#  plots  NDVI and NDRE
ndvi_plots <- list()
ndre_plots <- list()

for(pair in analysis_pairs) {
  # Create plot names
  plot_name <- paste0(
    "plot_",
    gsub("-", "_", pair$date),
    "_estab_",
    pair$estab_year
  )
  
  # Create NDVI plot
  ndvi_plots[[plot_name]] <- create_single_scatter_plot(
    ndvi_data26,
    pair$date,
    pair$biomass,
    pair$estab_year,
    "NDVI"
  )
  
  # Create NDRE plot
  ndre_plots[[plot_name]] <- create_single_scatter_plot(
    ndre_data26,
    pair$date,
    pair$biomass,
    pair$estab_year,
    "NDRE"
  )
}

# all plots
all_plots <- c(ndvi_plots, ndre_plots)

# Print summary of maximum index dates for each analysis
for(pair in analysis_pairs) {
  #  yield or biomass based on the target date
  target_month <- format(as.Date(pair$date), "%m")
  measurement_type <- if(target_month == "08") "Harvest Yield" else "Biomass"
  
  cat("\nNDVI Analysis for", measurement_type, "(Establishment Year:", pair$estab_year, "):\n")
  filtered_ndvi <- ndvi_data26 %>% 
    filter(Year_estab == pair$estab_year,
           Year_obs == as.numeric(format(as.Date(pair$date), "%Y")))
  max_ndvi_data <- get_max_index(filtered_ndvi, pair$date)
  cat("NDVI measurement dates:\n")
  print(table(max_ndvi_data$date_max))
  
  cat("\nNDRE Analysis for", measurement_type, "(Establishment Year:", pair$estab_year, "):\n")
  filtered_ndre <- ndre_data26 %>% 
    filter(Year_estab == pair$estab_year,
           Year_obs == as.numeric(format(as.Date(pair$date), "%Y")))
  max_ndre_data <- get_max_index(filtered_ndre, pair$date)
  cat("NDRE measurement dates:\n")
  print(table(max_ndre_data$date_max))
}
print(all_plots)
```

This is the corrected code - field 26

```{r}
# Function to get index values from the date with highest average index
get_max_index <- function(data, target_date) {
  # Convert target date
  target_date <- as.Date(target_date)
  
  # First find the date with highest average index across all treatments
  peak_date <- data %>%
    filter(as.Date(timestamp) <= target_date) %>%
    group_by(timestamp) %>%
    summarize(avg_index = mean(mean, na.rm = TRUE)) %>%
    slice_max(avg_index, n = 1) %>%
    pull(timestamp)
  
  # Then get the index values from that specific date
  index_values <- data %>%
    filter(timestamp == peak_date) %>%
    group_by(PLOT_ID) %>%
    summarize(
      max_index = mean(mean, na.rm = TRUE),  # using mean in case of multiple measurements on same date
      date_max = first(timestamp),
      Treatment = first(Treatment),
      Year_estab = first(Year_estab),
      .groups = 'drop'
    )
  
  return(index_values)
}

# Function to create scatter plot
create_single_scatter_plot <- function(data, target_date, biomass_col, estab_year, index_type="NDVI") {
  # Filter establishment observation year
  obs_year <- as.numeric(format(as.Date(target_date), "%Y"))
  
  plot_data <- data %>%
    filter(Year_estab == estab_year,
           Year_obs == obs_year)
  
  #  maximum values beforedate
  max_index_data <- get_max_index(plot_data, target_date)
  
  # biomass values per plot
  biomass_data <- plot_data %>%
    dplyr::select(PLOT_ID, !!sym(biomass_col)) %>%
    distinct()
  
  # Combine index and biomass data
  plot_data <- max_index_data %>%
    inner_join(biomass_data, by = "PLOT_ID")
  
  # Remove NA values
  plot_data <- na.omit(plot_data)
  
  # Calculate statistics 
  if(nrow(plot_data) >= 3) {
    # Fit model and get statistics
    model <- lm(get(biomass_col) ~ max_index, data = plot_data)
    r_squared <- round(summary(model)$r.squared, 3)
    correlation <- round(cor(plot_data$max_index, plot_data[[biomass_col]]), 3)
    p_value <- summary(model)$coefficients[2,4]  # Removed rounding
    slope <- round(coef(model)[2], 0)
    
    # Format dates
    target_date_str <- format(as.Date(target_date), "%d %B %Y")
    max_index_date <- format(as.Date(names(which.max(table(plot_data$date_max)))), "%d %B %Y")
    
    # Determine if this is harvest yield or biomass based on the target date
    target_month <- format(as.Date(target_date), "%m")
    measurement_type <- if(target_month == "08") "Harvest Yield" else "Biomass"
    
    # Format p-value with thresholds
    p_value_text <- if(p_value < 0.001) {
        "p < 0.001"
    } else if(p_value < 0.01) {
        "p < 0.01"
    } else if(p_value < 0.05) {
        "p < 0.05"
    } else {
        sprintf("p = %.3f", p_value)
    }
    
    p <- ggplot(plot_data, aes(x = max_index, y = .data[[biomass_col]], color = Treatment)) +
      geom_point(alpha = 0.6, size = 3) +
      geom_smooth(method = "lm", color = "black", se = TRUE, linewidth = 1) +
      theme_minimal() +
      scale_color_manual(values = treatment_colors) +
      labs(
        title = paste(index_type, "vs", measurement_type, "-", "Establishment Year:", estab_year),
        subtitle = paste0(
          "Max ", index_type, " from: ", max_index_date, "  |  ",
          measurement_type, " from: ", target_date_str, "\n",
          "R = ", r_squared, "  |  ",
          p_value_text, "  |  ",  # Changed to use p_value_text directly
          "Correlation = ", correlation
        ),
        x = paste("Maximum", index_type),
        y = paste(measurement_type, "(kg/ha)")
      ) +
      theme(
        plot.title = element_text(size = 11, face = "bold"),
        plot.subtitle = element_text(size = 9),
        axis.title = element_text(size = 10),
        legend.position = "bottom",
        plot.margin = margin(t = 10, r = 10, b = 10, l = 10)
      )
    
    return(p)
  }
}

# Define analysis pairs
analysis_pairs <- list(
  list(
    date = "2021-06-23",
    biomass = "Anthesis_23062021_Biomass_dryweight_kgha",
    estab_year = 2021
  ),
  list(
    date = "2021-08-06",
    biomass = "Harvest_06082021_harvestable_grain_yield_15_moisture_kgha",
    estab_year = 2021
  ),
  list(
    date = "2022-05-31",
    biomass = "Anthesis_31052022_Biomass_dryweight_kgha",
    estab_year = 2022
  ),
  list(
    date = "2022-08-11",
    biomass = "Harvest_11082022_harvestable_grain_yield_15_moisture_kgha",
    estab_year = 2022
  )
)

#  plots  NDVI and NDRE
ndvi_plots <- list()
ndre_plots <- list()

for(pair in analysis_pairs) {
  # Create plot names
  plot_name <- paste0(
    "plot_",
    gsub("-", "_", pair$date),
    "_estab_",
    pair$estab_year
  )
  
  # Create NDVI plot
  ndvi_plots[[plot_name]] <- create_single_scatter_plot(
    ndvi_data26,
    pair$date,
    pair$biomass,
    pair$estab_year,
    "NDVI"
  )
  
  # Create NDRE plot
  ndre_plots[[plot_name]] <- create_single_scatter_plot(
    ndre_data26,
    pair$date,
    pair$biomass,
    pair$estab_year,
    "NDRE"
  )
}

# all plots
all_plots <- c(ndvi_plots, ndre_plots)

# Print summary of maximum index dates for each analysis
for(pair in analysis_pairs) {
  # Determine if this is harvest yield or biomass based on the target date
  target_month <- format(as.Date(pair$date), "%m")
  measurement_type <- if(target_month == "08") "Harvest Yield" else "Biomass"
  
  cat("\nNDVI Analysis for", measurement_type, "(Establishment Year:", pair$estab_year, "):\n")
  filtered_ndvi <- ndvi_data26 %>% 
    filter(Year_estab == pair$estab_year,
           Year_obs == as.numeric(format(as.Date(pair$date), "%Y")))
  max_ndvi_data <- get_max_index(filtered_ndvi, pair$date)
  cat("NDVI measurement dates:\n")
  print(table(max_ndvi_data$date_max))
  
  cat("\nNDRE Analysis for", measurement_type, "(Establishment Year:", pair$estab_year, "):\n")
  filtered_ndre <- ndre_data26 %>% 
    filter(Year_estab == pair$estab_year,
           Year_obs == as.numeric(format(as.Date(pair$date), "%Y")))
  max_ndre_data <- get_max_index(filtered_ndre, pair$date)
  cat("NDRE measurement dates:\n")
  print(table(max_ndre_data$date_max))
}
print(all_plots)
```

#### Harvest largeplot trial 

```{r}
# Function to create annotation text with stats
create_stats_annotation <- function(data, x_var, y_var) {
  df <- data.frame(
    x = data[[x_var]],
    y = data[[y_var]]
  )
  
  lm_model <- lm(y ~ x, data = df)
  
  correlation <- cor(df$x, df$y)  # Calculate correlation
  slope <- coef(lm_model)[2]
  p_value <- summary(lm_model)$coefficients[2,4]
  
  # Format p-value with thresholds
  p_value_text <- if(p_value < 0.001) {
    "p < 0.001"
  } else if(p_value < 0.01) {
    "p < 0.01"
  } else if(p_value < 0.05) {
    "p < 0.05"
  } else {
    sprintf("p = %.3f", p_value)
  }
  
  annotation <- sprintf(
    "Correlation = %.3f\nSlope = %.3f\n%s",
    correlation, slope, p_value_text
  )
  
  return(annotation)
}

# Function to analyze vegetation indices
create_ndvi_analysis <- function(data, input_name) {
  data$timestamp <- as.Date(data$timestamp)
  
  daily_means <- data %>%
    group_by(timestamp) %>%
    summarise(daily_mean = mean(mean, na.rm = TRUE)) %>%
    arrange(desc(daily_mean))
  
  peak_date_2021 <- daily_means %>%
    filter(year(timestamp) == 2021) %>%
    slice(1) %>%
    pull(timestamp)
  
  peak_date_2022 <- daily_means %>%
    filter(year(timestamp) == 2022) %>%
    slice(1) %>%
    pull(timestamp)
  
  areas <- data %>%
    group_by(PLOT_ID) %>%
    summarise(
      peak_value_2021 = mean(mean[timestamp == peak_date_2021], na.rm = TRUE),
      peak_value_2022 = mean(mean[timestamp == peak_date_2022], na.rm = TRUE),
      
      Treatment_2021 = first(Treatment_2021),
      Treatment_2022 = first(Treatment_2022),
      Block_a = first(Block_a),
      Block_b = first(Block_b),
      
      Harvest_2021 = first(Harvest_06082021_harvestable_grain_yield_15_moisture_kgha),
      Harvest_2022 = first(Harvest_11082022_harvestable_grain_yield_15_moisture_kgha),
      
      plot_number = first(plot_number),
      country.x = first(country.x)
    )
  
  new_name <- paste0(input_name, "_analysis")
  assign(new_name, areas, envir = .GlobalEnv)
  write.csv(areas, file = paste0(new_name, ".csv"), row.names = FALSE)
  
  cat("Peak dates used:\n")
  cat("2021:", as.character(peak_date_2021), "\n")
  cat("2022:", as.character(peak_date_2022), "\n")
  
  return(list(data = areas, peak_dates = list(peak_2021 = peak_date_2021, peak_2022 = peak_date_2022)))
}

# Run analyses
ndvi_results <- create_ndvi_analysis(ndvi_data25_2, "ndvi_data25_2")
ndre_results <- create_ndvi_analysis(ndre_data25_2, "ndre_data25_2")

# Create NDVI plots
ndvi_p1 <- ggplot(ndvi_results$data, aes(x = peak_value_2021, y = Harvest_2021)) +
  geom_point(aes(color = Treatment_2021), size = 3, alpha = 0.7) +
  geom_smooth(method = "lm", se = TRUE, color = "black", linetype = "dashed") +
  scale_color_manual(values = treatment_colors, labels = treatment_labels_lp) +
  labs(title = "2021 Peak NDVI vs Harvest Yield",
       x = paste0("NDVI on ", ndvi_results$peak_dates$peak_2021),
       y = "Harvest Yield 2021 (kg/ha)",
       color = "Treatment") +
  my_theme +
  theme(legend.position = "none") +
  annotate("text", 
           x = min(ndvi_results$data$peak_value_2021, na.rm = TRUE),
           y = max(ndvi_results$data$Harvest_2021, na.rm = TRUE),
           label = create_stats_annotation(ndvi_results$data, "peak_value_2021", "Harvest_2021"),
           hjust = 0, vjust = 1)

ndvi_p2 <- ggplot(ndvi_results$data, aes(x = peak_value_2022, y = Harvest_2022)) +
  geom_point(aes(color = Treatment_2022), size = 3, alpha = 0.7) +
  geom_smooth(method = "lm", se = TRUE, color = "black", linetype = "dashed") +
  scale_color_manual(values = treatment_colors, labels = treatment_labels_lp) +
  labs(title = "2022 Peak NDVI vs Harvest Yield",
       x = paste0("NDVI on ", ndvi_results$peak_dates$peak_2022),
       y = "Harvest Yield 2022 (kg/ha)",
       color = "Treatment") +
  my_theme +
  annotate("text",
           x = min(ndvi_results$data$peak_value_2022, na.rm = TRUE),
           y = max(ndvi_results$data$Harvest_2022, na.rm = TRUE),
           label = create_stats_annotation(ndvi_results$data, "peak_value_2022", "Harvest_2022"),
           hjust = 0, vjust = 1)

# Create NDRE plots
ndre_p1 <- ggplot(ndre_results$data, aes(x = peak_value_2021, y = Harvest_2021)) +
  geom_point(aes(color = Treatment_2021), size = 3, alpha = 0.7) +
  geom_smooth(method = "lm", se = TRUE, color = "black", linetype = "dashed") +
  scale_color_manual(values = treatment_colors, labels = treatment_labels_lp) +
  labs(title = "2021 Peak NDRE vs Harvest Yield",
       x = paste0("NDRE on ", ndre_results$peak_dates$peak_2021),
       y = "Harvest Yield 2021 (kg/ha)",
       color = "Treatment") +
  my_theme +
  theme(legend.position = "none") +
  annotate("text", 
           x = min(ndre_results$data$peak_value_2021, na.rm = TRUE),
           y = max(ndre_results$data$Harvest_2021, na.rm = TRUE),
           label = create_stats_annotation(ndre_results$data, "peak_value_2021", "Harvest_2021"),
           hjust = 0, vjust = 1)

ndre_p2 <- ggplot(ndre_results$data, aes(x = peak_value_2022, y = Harvest_2022)) +
  geom_point(aes(color = Treatment_2022), size = 3, alpha = 0.7) +
  geom_smooth(method = "lm", se = TRUE, color = "black", linetype = "dashed") +
  scale_color_manual(values = treatment_colors, labels = treatment_labels_lp) +
  labs(title = "2022 Peak NDRE vs Harvest Yield",
       x = paste0("NDRE on ", ndre_results$peak_dates$peak_2022),
       y = "Harvest Yield 2022 (kg/ha)",
       color = "Treatment") +
  my_theme +
  annotate("text",
           x = min(ndre_results$data$peak_value_2022, na.rm = TRUE),
           y = max(ndre_results$data$Harvest_2022, na.rm = TRUE),
           label = create_stats_annotation(ndre_results$data, "peak_value_2022", "Harvest_2022"),
           hjust = 0, vjust = 1)

print(ndvi_p1)
print(ndre_p1)
print(ndvi_p2) 
print(ndre_p2)
```

```{r}
# Prepare datasets for both years
data_2021 <- reflectance_soiloptix_largeplot25_satelite %>%
  filter(timestamp >= start_date_sb,
         timestamp <= end_date_sb) %>%
  mutate(Treatment = Treatment_2021,
         timeSinceStart = as.numeric(timestamp - start_date_sb))

data_2022 <- reflectance_soiloptix_largeplot25_satelite %>%
  filter(timestamp >= start_date_ww,
         timestamp <= end_date_ww) %>%
  mutate(Treatment = Treatment_2022,
         timeSinceStart = as.numeric(timestamp - start_date_ww))

# Function to fit models for both indices
fit_models <- function(data, index, param) {
  # Formula for models
  formula_int <- as.formula(paste(index, "~ Treatment * timeSinceStart *", param, ""))
  formula_no_int <- as.formula(paste(index, "~ Treatment * timeSinceStart + ", param, ""))
  
  # Fit models
  model_int <- lme(formula_int,
                  random = ~1|PLOT_ID,
                  correlation = corAR1(form = ~timeSinceStart|PLOT_ID),
                  data = data)
  
  model_no_int <- lme(formula_no_int,
                     random = ~1|PLOT_ID,
                     correlation = corAR1(form = ~timeSinceStart|PLOT_ID),
                     data = data)
  
  # Compare models
  comparison <- anova(model_int, model_no_int)
  
  return(list(
    int = model_int,
    no_int = model_no_int,
    comparison = comparison
  ))
}

# Fit models for all parameters and both indices
params <- c("clay", "humus", "ph", "fineSand")
indices <- c("NDVI", "NDRE")
years <- list("2021" = data_2021, "2022" = data_2022)

# Store all model results
all_models <- list()
for(year_name in names(years)) {
  all_models[[year_name]] <- list()
  for(index in indices) {
    all_models[[year_name]][[index]] <- list()
    for(param in params) {
      all_models[[year_name]][[index]][[param]] <- 
        fit_models(years[[year_name]], index, param)
    }
  }
}

# Function to create plots with updated styling
create_index_plot <- function(data, index, year) {
  p <- ggplot(data, aes(x = timeSinceStart, y = get(index), color = Treatment)) +
    geom_point(alpha = 0.5) +
    geom_smooth() +
    facet_wrap(~cut(clay, breaks = 3),
              labeller = labeller(
                clay = function(x) paste("Clay Content:", x, "%")
              )) +
    my_theme +  # Apply your custom theme
    labs(title = paste(year, index, "over time by Treatment and Clay Content"),
         x = paste("Days since", ifelse(year == "2021", "April 1st, 2021", "March 30th, 2022")),
         y = index)
  
  # Only add horizontal bottom legend for 2022
  if(year == "2022") {
    p <- p + theme(
      legend.position = "bottom",
      legend.direction = "horizontal",
      legend.box = "horizontal",
      legend.margin = margin(t = 20)  # Add some space above the legend
    )
  } else {
    p <- p + theme(legend.position = "none")  # Remove legend for 2021
  }
  
  return(p)
}

# Extract results for table
extract_model_results <- function(models) {
  results <- data.frame(
    Index = character(),
    Year = character(),
    Parameter = character(),
    L_Ratio = numeric(),
    p_value = character(),
    stringsAsFactors = FALSE
  )
  
  for(year_name in names(models)) {
    for(index in names(models[[year_name]])) {
      for(param in names(models[[year_name]][[index]])) {
        comparison <- models[[year_name]][[index]][[param]]$comparison
        
        results <- rbind(results, data.frame(
          Index = index,
          Year = year_name,
          Parameter = case_when(
            param == "ph" ~ "pH",
            param == "fineSand" ~ "Fine Sand",
            TRUE ~ str_to_title(param)
          ),
          L_Ratio = comparison$L.Ratio[2],
          p_value = ifelse(comparison$`p-value`[2] < 0.001,
                          "< 0.001",
                          sprintf("%.3f", comparison$`p-value`[2]))
        ))
      }
    }
  }
  
  return(results)
}

# Create and format table
model_results <- extract_model_results(all_models) %>%
  mutate(
    H_0 = "Reflectance ~ Treatment  Time + Parameter",
    H_1 = "Reflectance ~ Treatment  time  Parameter"
  )

# Create formatted table
formatted_table <- model_results %>%
  arrange(Index, Year, Parameter) %>%
  kbl(format = "latex",
      caption = "Tests for Treatment and Soil Parameter Interactions (Field 25)",
      label = "soil_parameter_interactions_field25",
      col.names = c("Vegetation Index", "Year", "Soil Parameter", "L.Ratio", 
                   "$p$-value", "$H_0$", "$H_1$"),
      align = c('l', 'c', 'l', 'c', 'c', 'l', 'l'),
      booktabs = TRUE,
      escape = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position")) %>%
  add_header_above(c(
    "Identification" = 3,
    "Model Test" = 2,
    "Test" = 2
  )) %>%
  pack_rows("NDRE", 1, 8) %>%
  pack_rows("NDVI", 9, 16) %>%
  row_spec(8, extra_latex_after = "\\midrule") %>%
  footnote(
    general = "Random effect (1|PLOT ID) is included in all models.",
    escape = FALSE
  )

print("Model Results Table:")
print(model_results)

# Print comparison results for each case
for(year_name in names(all_models)) {
  for(index in indices) {
    for(param in params) {
      cat("\nResults for", year_name, "-", index, "-", param, ":\n")
      print(all_models[[year_name]][[index]][[param]]$comparison)
    }
  }
}

# Create and print QQ plots for model diagnostics
for(year_name in names(all_models)) {
  for(index in indices) {
    for(param in params) {
      # QQ plot for model with interaction
      qq_int <- ggplot(data.frame(resid = residuals(all_models[[year_name]][[index]][[param]]$int)), 
                      aes(sample = resid)) +
        stat_qq() +
        stat_qq_line() +
        labs(title = paste(index, year_name, param, "- Model with interaction"),
             x = "Theoretical Quantiles",
             y = "Sample Quantiles")
      print(qq_int)
      
      # QQ plot for model without interaction
      qq_no_int <- ggplot(data.frame(resid = residuals(all_models[[year_name]][[index]][[param]]$no_int)), 
                         aes(sample = resid)) +
        stat_qq() +
        stat_qq_line() +
        labs(title = paste(index, year_name, param, "- Model without interaction"),
             x = "Theoretical Quantiles",
             y = "Sample Quantiles")
      print(qq_no_int)
    }
  }
}

# Print summary of a few example models
cat("\nExample Model Summaries:\n")
print(summary(all_models[["2022"]][["NDVI"]][["clay"]]$int))
print(summary(all_models[["2022"]][["NDRE"]][["clay"]]$int))

# Create and print main plots
for(year_name in names(years)) {
  for(index in indices) {
    main_plot <- create_index_plot(years[[year_name]], index, year_name)
    print(main_plot)
  }
}

# Create and print residual plots
for(year_name in names(all_models)) {
  for(index in indices) {
    for(param in params) {
      # Residual plot for model with interaction
      res_int <- ggplot(data.frame(
        fitted = fitted(all_models[[year_name]][[index]][[param]]$int),
        resid = residuals(all_models[[year_name]][[index]][[param]]$int),
        Treatment = years[[year_name]]$Treatment), 
        aes(x = fitted, y = resid, color = Treatment)) +
        geom_point(alpha = 0.5) +
        geom_smooth(method = "loess", se = FALSE) +
        geom_hline(yintercept = 0, linetype = "dashed") +
        scale_color_manual(values = treatment_colors) +
        my_theme +
        labs(title = paste(index, year_name, param, "- Residuals (with interaction)"),
             x = "Fitted values",
             y = "Residuals")
      print(res_int)
      
      # Residual plot for model without interaction
      res_no_int <- ggplot(data.frame(
        fitted = fitted(all_models[[year_name]][[index]][[param]]$no_int),
        resid = residuals(all_models[[year_name]][[index]][[param]]$no_int),
        Treatment = years[[year_name]]$Treatment), 
        aes(x = fitted, y = resid, color = Treatment)) +
        geom_point(alpha = 0.5) +
        geom_smooth(method = "loess", se = FALSE) +
        geom_hline(yintercept = 0, linetype = "dashed") +
        scale_color_manual(values = treatment_colors) +
        my_theme +
        labs(title = paste(index, year_name, param, "- Residuals (without interaction)"),
             x = "Fitted values",
             y = "Residuals")
      print(res_no_int)
    }
  }
}
```
